# AP Exam Formula Sheet

```{r}
library(tidyverse)
```

[Here is the original AP Statistics Formula Sheet developed by Collegeboard.](https://apcentral.collegeboard.org/media/pdf/statistics-formula-sheet-and-tables-2020.pdf)

## Descriptive Statistics

$$
\begin{aligned}
\bar x &= \frac{1}{n}\sum x_i = \frac{\sum x_i}{n} \\\\
s_x &= \sqrt{\frac{1}{n-1}\sum (x_i - \bar x)^2} = \sqrt{\frac{\sum(x_i -\bar x)^2}{n - 1}}\\\\
\hat y &= a + bx \\\\
\bar y &= a + b \bar x\\\\
r &= \frac{1}{n-1}\sum \left( \frac{x_i - \bar x}{s_x}\right) \left( \frac{y_i -\bar y}{s_y}\right)\\\\
b &= r \frac{s_y}{s_x}
\end{aligned}
$$

## Probability and Distributions

$$
\begin{aligned}
P(A \cup B) &= P(A) + P(B) - P(A \cap B) \\\\
P(A | B) &= \frac{P(A \cap B)}{P(B)}
\end{aligned}
$$

| Probability Distribution                                                                                                                                | Mean                                              | Standard Deviation                                                         |
|---------------------------------------------------------------------------------------------------------------------------------------------------------|---------------------------------------------------|----------------------------------------------------------------------------|
| Discrete random variable, $X$                                                                                                                           | $\mu_X = E(X) = \sum x_i P(x_i)$ | $\sigma_X = \sqrt{\sum \left( x_i - \mu_X \right) ^2 P \left( x_i \right)}$ |
| If $X$ has a **binomial distribution**  with parameters $n$ and $p$, then: <br>$$P(X = x) = {n \choose x} p^x (1 - p)^{n - x}$$  <br>where $x = 0, 1, 2, 3, ..., n$ | $\mu_X = np$                                      | $\sigma_X = \sqrt{np(1-p)}$                                                  |
| If $X$ has a **geometric distribution** with parameter $p$, then: <br>$$P(X = x) = (1 - p)^{x - 1} p$$ <br>where $x = 1, 2, 3, ...$                               | $\mu_X = \frac{1}{p}$                             | $\sigma_X = \frac{\sqrt{1-p}}{p}$                                           |

## Sampling Distributions and Inferential Statistics

$$\text{Standardized test statistic:}~~~~ \frac{\text{statistic} - \text{parameter}} {\text{standard error of the statistic}}$$\

$$\text{Confidence interval:}~~~~ \text{statistic} \pm (\text{critical value}) (\text{standard error of statistic})$$\

$$\text{Chi-square statistic:}~~~~ \chi^2 = \sum \frac{(\text{observed} - \text{expected})^2}{\text{expected}}$$

### Sampling distributions for proportions:

| Random Variable                               | Parameters of Sampling Distribution (mean) | Parameters of Sampling Distribution (standard deviation)                               | Standard Error* of Sample Statistic                                                                                                                                                                                                                                                                 |
|-----------------------------------------------|--------------------------------------------|----------------------------------------------------------------------------------------|-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| For one population: <br>$\hat p$              | $\mu_{\hat p} = p$                         | $\sigma_{\hat p} = \sqrt{\frac{p(1-p)}{n}}$                                            | $s_{\hat p} = \sqrt{\frac{\hat p (1 - \hat p)}{n}}$                                                                                                                                                                                                                                                 |
| For two populations:<br>$\hat p_1 - \hat p_2$ | $\mu_{\hat p_1 - \hat p_2} = p_1 - p_2$    | $\sigma_{\hat p_1 - \hat p_2}= \sqrt{\frac{p_1(1-p_1)}{n_1} + \frac{p_2(1-p_2)}{n_2}}$ | $s_{\hat p_1 - \hat p_2}= \sqrt{\frac{\hat p_1(1- \hat p_1)}{n_1} + \frac{\hat p_2(1- \hat p_2)}{n_2}}$<br><br>When $p_1 = p_2$ is assumed:<br><br>$s_{\hat p_1 -\hat p_2} = \sqrt{\hat p_c (1 - \hat p_c) \left( \frac{1}{n_1} + \frac{1}{n_2} \right)}$<br><br>where $\hat p_c = \frac{X_1 + X_2}{n_1 + n_2}$ |

### Sampling distributions for means:

| Random Variable                               | Parameters of Sampling Distribution (mean)  | Parameters of Sampling Distribution (standard deviation)                                | Standard Error* of Sample Statistic                                      |
|-----------------------------------------------|---------------------------------------------|-----------------------------------------------------------------------------------------|--------------------------------------------------------------------------|
| For one population: <br>$\overline{X}$              | $\mu_{\overline X} = \mu$                        | $\sigma_{\overline X} = \frac{\sigma}{\sqrt n}$                                              | $s_{\overline X} = \frac{s}{\sqrt n}$                                         |
| For two populations:<br>$\overline{X_1} - \overline{X_2}$ | $\mu_{\overline{X_1} - \overline{X_2}} = \mu_1 - \mu_2$ | $\sigma_{\overline{X_1} - \overline{X_2}} = \sqrt{\frac{\sigma_1^2}{n_1} + \frac{\sigma_2^2}{n_2}}$ | $s_{\overline{X_1} - \overline{X_2}} = \sqrt{\frac{s_1^2}{n_1} + \frac{s_2^2}{n_2}}$ |

### Sampling distributions for simple linear regression:

| Random Variable   | Parameters of Sampling Distribution (mean) | Parameters of Sampling Distribution (standard deviation)                                                         | Standard Error* of Sample Statistic                                                                                                                                 |
|-------------------|--------------------------------------------|------------------------------------------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| For slope:<br>$b$ | $\mu_b = \beta$                            | $\sigma_{b} = \frac{\sigma}{\sigma_x \sqrt n}$,<br><br>where $\sigma_x = \sqrt{\frac{\sum (x_i - \bar x)^2}{n}}$ | $s_{b} = \frac{s}{s_x \sqrt{n-1}}$ ,<br><br>where $s = \sqrt{\frac{\sum (y_i - \hat y_i)^2)}{n - 2}}$<br><br>and $s_x = \sqrt{\frac{\sum (x_i - \bar x)^2}{n - 1}}$ |

*Standard deviation is a measurement of variability from the theoretical population. Standard error is the estimate of the standard deviation. If the standard deviation of the statistic is assumed to be known, then the standard deviation should be used instead of the standard error.

## Table A: Standard normal probabilities {#table-a}

```{r Standard normal dist table calc, echo = FALSE, results='asis'}
# library(stargazer)
# 
# neg_vals = format(round(pnorm(seq(-3.49, 0, 0.01)), dig = 4), nsmall = 4)
# neg_vals_df = data.frame(replicate(10, numeric(35)))
# rownames(neg_vals_df) <- paste0("-", format(rev(seq(0, 3.4, 0.1)), nsmall = 1))
# colnames(neg_vals_df) <- format(seq(0, .09, .01), nsmall = 2)
# for (i in 0:9) {
#     neg_vals_df[[i + 1]] = neg_vals[seq(10 - i, by = 10, length = 35)]
# }
# 
# 
# pos_vals = format(round(pnorm(seq(0, 3.49, 0.01)), dig = 4), nsmall = 4)
# pos_vals_df = data.frame(replicate(10, numeric(35)))
# rownames(pos_vals_df) <- paste0(format(seq(0, 3.4, 0.1), nsmall = 1))
# colnames(pos_vals_df) <- format(seq(0, .09, .01), nsmall = 2)
# for (i in 1:10) {
#     pos_vals_df[[i]] = pos_vals[seq(i, by = 10, length = 35)]
# }
# 
# write.csv(neg_vals_df, "z_neg_vals.csv")
# write.csv(pos_vals_df, "z_pos_vals.csv")

```

```{r Standard normal dist table, echo = FALSE}
ggplot() + xlim(-4,4) +
    geom_polygon(aes(x = c(-4, seq(-4,-1,0.01), -1), 
                     y = c(0, dnorm(seq(-4, -1, 0.01)), 0)), 
                 alpha = 0.5) +
    stat_function(fun = dnorm, size = 1.2, n = 1000) + theme_void() +
    annotate("segment", x = -1, xend = -1, y = -.01, yend = .01, size = 1.1) + 
    annotate("text", x = -1, y = -.025, label = "z") +
    annotate("segment", x = -2.5, y = .2, xend = -1.5, yend = .05, arrow = arrow(), size = 1.1) +
    annotate("text", x = -2.5, y = 0.225, label =  "Probability p")

# x <- seq(-4,4,0.01)
# x.1 <- seq(-4,-1,0.01)
# par(mar=c(3,1,1,1))
# plot.new()
# plot.window(c(-4, 4), c(0, .4))
# lines(x, dnorm(x), lwd = 1.5)
# polygon(c(x.1, x.1[length(x.1)]), c(dnorm(x.1), 0), col = "gray")
# axis(side = 1, at = -1, labels = expression(z))
# arrows(-2.5, .2, -1.5, 0.05, lwd = 1.5)
# text(-2.5, .225, "Probability")
# box()
```

<details>
  <summary> Click for table of standard normal probabilities </summary>

Table entry for $z$ is the probability lying below $z$.

<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;width:100%;}
.tg td{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  overflow:hidden;padding:10px 5px;word-break:normal;}
.tg th{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-5aeg{background-color:#C0C0C0;border-color:#000000;font-family:"Lucida Console", Monaco, monospace !important;
  text-align:center;vertical-align:bottom}
.tg .tg-fb3z{background-color:#343434;border-color:#000000;color:#FFF;font-family:"Lucida Console", Monaco, monospace !important;
  font-weight:bold;text-align:center;vertical-align:bottom}
.tg .tg-hxgm{border-color:#000000;font-family:"Lucida Console", Monaco, monospace !important;text-align:center;vertical-align:bottom
  }
</style>
<table class="tg">
<thead>
  <tr>
    <th class="tg-fb3z">$z$</th>
    <th class="tg-fb3z">0.00</th>
    <th class="tg-fb3z">0.01</th>
    <th class="tg-fb3z">0.02</th>
    <th class="tg-fb3z">0.03</th>
    <th class="tg-fb3z">0.04</th>
    <th class="tg-fb3z">0.05</th>
    <th class="tg-fb3z">0.06</th>
    <th class="tg-fb3z">0.07</th>
    <th class="tg-fb3z">0.08</th>
    <th class="tg-fb3z">0.09</th>
  </tr>
</thead>
<tbody>
  <tr>
    <td class="tg-fb3z">-3.4</td>
    <td class="tg-hxgm">0.0003</td>
    <td class="tg-hxgm">0.0003</td>
    <td class="tg-hxgm">0.0003</td>
    <td class="tg-hxgm">0.0003</td>
    <td class="tg-hxgm">0.0003</td>
    <td class="tg-hxgm">0.0003</td>
    <td class="tg-hxgm">0.0003</td>
    <td class="tg-hxgm">0.0003</td>
    <td class="tg-hxgm">0.0003</td>
    <td class="tg-hxgm">0.0002</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-3.3</td>
    <td class="tg-5aeg">0.0005</td>
    <td class="tg-5aeg">0.0005</td>
    <td class="tg-5aeg">0.0005</td>
    <td class="tg-5aeg">0.0004</td>
    <td class="tg-5aeg">0.0004</td>
    <td class="tg-5aeg">0.0004</td>
    <td class="tg-5aeg">0.0004</td>
    <td class="tg-5aeg">0.0004</td>
    <td class="tg-5aeg">0.0004</td>
    <td class="tg-5aeg">0.0003</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-3.2</td>
    <td class="tg-hxgm">0.0007</td>
    <td class="tg-hxgm">0.0007</td>
    <td class="tg-hxgm">0.0006</td>
    <td class="tg-hxgm">0.0006</td>
    <td class="tg-hxgm">0.0006</td>
    <td class="tg-hxgm">0.0006</td>
    <td class="tg-hxgm">0.0006</td>
    <td class="tg-hxgm">0.0005</td>
    <td class="tg-hxgm">0.0005</td>
    <td class="tg-hxgm">0.0005</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-3.1</td>
    <td class="tg-5aeg">0.0010</td>
    <td class="tg-5aeg">0.0009</td>
    <td class="tg-5aeg">0.0009</td>
    <td class="tg-5aeg">0.0009</td>
    <td class="tg-5aeg">0.0008</td>
    <td class="tg-5aeg">0.0008</td>
    <td class="tg-5aeg">0.0008</td>
    <td class="tg-5aeg">0.0008</td>
    <td class="tg-5aeg">0.0007</td>
    <td class="tg-5aeg">0.0007</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-3.0</td>
    <td class="tg-hxgm">0.0013</td>
    <td class="tg-hxgm">0.0013</td>
    <td class="tg-hxgm">0.0013</td>
    <td class="tg-hxgm">0.0012</td>
    <td class="tg-hxgm">0.0012</td>
    <td class="tg-hxgm">0.0011</td>
    <td class="tg-hxgm">0.0011</td>
    <td class="tg-hxgm">0.0011</td>
    <td class="tg-hxgm">0.0010</td>
    <td class="tg-hxgm">0.0010</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-2.9</td>
    <td class="tg-5aeg">0.0019</td>
    <td class="tg-5aeg">0.0018</td>
    <td class="tg-5aeg">0.0018</td>
    <td class="tg-5aeg">0.0017</td>
    <td class="tg-5aeg">0.0016</td>
    <td class="tg-5aeg">0.0016</td>
    <td class="tg-5aeg">0.0015</td>
    <td class="tg-5aeg">0.0015</td>
    <td class="tg-5aeg">0.0014</td>
    <td class="tg-5aeg">0.0014</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-2.8</td>
    <td class="tg-hxgm">0.0026</td>
    <td class="tg-hxgm">0.0025</td>
    <td class="tg-hxgm">0.0024</td>
    <td class="tg-hxgm">0.0023</td>
    <td class="tg-hxgm">0.0023</td>
    <td class="tg-hxgm">0.0022</td>
    <td class="tg-hxgm">0.0021</td>
    <td class="tg-hxgm">0.0021</td>
    <td class="tg-hxgm">0.0020</td>
    <td class="tg-hxgm">0.0019</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-2.7</td>
    <td class="tg-5aeg">0.0035</td>
    <td class="tg-5aeg">0.0034</td>
    <td class="tg-5aeg">0.0033</td>
    <td class="tg-5aeg">0.0032</td>
    <td class="tg-5aeg">0.0031</td>
    <td class="tg-5aeg">0.0030</td>
    <td class="tg-5aeg">0.0029</td>
    <td class="tg-5aeg">0.0028</td>
    <td class="tg-5aeg">0.0027</td>
    <td class="tg-5aeg">0.0026</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-2.6</td>
    <td class="tg-hxgm">0.0047</td>
    <td class="tg-hxgm">0.0045</td>
    <td class="tg-hxgm">0.0044</td>
    <td class="tg-hxgm">0.0043</td>
    <td class="tg-hxgm">0.0041</td>
    <td class="tg-hxgm">0.0040</td>
    <td class="tg-hxgm">0.0039</td>
    <td class="tg-hxgm">0.0038</td>
    <td class="tg-hxgm">0.0037</td>
    <td class="tg-hxgm">0.0036</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-2.5</td>
    <td class="tg-5aeg">0.0062</td>
    <td class="tg-5aeg">0.0060</td>
    <td class="tg-5aeg">0.0059</td>
    <td class="tg-5aeg">0.0057</td>
    <td class="tg-5aeg">0.0055</td>
    <td class="tg-5aeg">0.0054</td>
    <td class="tg-5aeg">0.0052</td>
    <td class="tg-5aeg">0.0051</td>
    <td class="tg-5aeg">0.0049</td>
    <td class="tg-5aeg">0.0048</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-2.4</td>
    <td class="tg-hxgm">0.0082</td>
    <td class="tg-hxgm">0.0080</td>
    <td class="tg-hxgm">0.0078</td>
    <td class="tg-hxgm">0.0075</td>
    <td class="tg-hxgm">0.0073</td>
    <td class="tg-hxgm">0.0071</td>
    <td class="tg-hxgm">0.0069</td>
    <td class="tg-hxgm">0.0068</td>
    <td class="tg-hxgm">0.0066</td>
    <td class="tg-hxgm">0.0064</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-2.3</td>
    <td class="tg-5aeg">0.0107</td>
    <td class="tg-5aeg">0.0104</td>
    <td class="tg-5aeg">0.0102</td>
    <td class="tg-5aeg">0.0099</td>
    <td class="tg-5aeg">0.0096</td>
    <td class="tg-5aeg">0.0094</td>
    <td class="tg-5aeg">0.0091</td>
    <td class="tg-5aeg">0.0089</td>
    <td class="tg-5aeg">0.0087</td>
    <td class="tg-5aeg">0.0084</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-2.2</td>
    <td class="tg-hxgm">0.0139</td>
    <td class="tg-hxgm">0.0136</td>
    <td class="tg-hxgm">0.0132</td>
    <td class="tg-hxgm">0.0129</td>
    <td class="tg-hxgm">0.0125</td>
    <td class="tg-hxgm">0.0122</td>
    <td class="tg-hxgm">0.0119</td>
    <td class="tg-hxgm">0.0116</td>
    <td class="tg-hxgm">0.0113</td>
    <td class="tg-hxgm">0.0110</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-2.1</td>
    <td class="tg-5aeg">0.0179</td>
    <td class="tg-5aeg">0.0174</td>
    <td class="tg-5aeg">0.017</td>
    <td class="tg-5aeg">0.0166</td>
    <td class="tg-5aeg">0.0162</td>
    <td class="tg-5aeg">0.0158</td>
    <td class="tg-5aeg">0.0154</td>
    <td class="tg-5aeg">0.0150</td>
    <td class="tg-5aeg">0.0146</td>
    <td class="tg-5aeg">0.0143</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-2.0</td>
    <td class="tg-hxgm">0.0228</td>
    <td class="tg-hxgm">0.0222</td>
    <td class="tg-hxgm">0.0217</td>
    <td class="tg-hxgm">0.0212</td>
    <td class="tg-hxgm">0.0207</td>
    <td class="tg-hxgm">0.0202</td>
    <td class="tg-hxgm">0.0197</td>
    <td class="tg-hxgm">0.0192</td>
    <td class="tg-hxgm">0.0188</td>
    <td class="tg-hxgm">0.0183</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-1.9</td>
    <td class="tg-5aeg">0.0287</td>
    <td class="tg-5aeg">0.0281</td>
    <td class="tg-5aeg">0.0274</td>
    <td class="tg-5aeg">0.0268</td>
    <td class="tg-5aeg">0.0262</td>
    <td class="tg-5aeg">0.0256</td>
    <td class="tg-5aeg">0.0250</td>
    <td class="tg-5aeg">0.0244</td>
    <td class="tg-5aeg">0.0239</td>
    <td class="tg-5aeg">0.0233</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-1.8</td>
    <td class="tg-hxgm">0.0359</td>
    <td class="tg-hxgm">0.0351</td>
    <td class="tg-hxgm">0.0344</td>
    <td class="tg-hxgm">0.0336</td>
    <td class="tg-hxgm">0.0329</td>
    <td class="tg-hxgm">0.0322</td>
    <td class="tg-hxgm">0.0314</td>
    <td class="tg-hxgm">0.0307</td>
    <td class="tg-hxgm">0.0301</td>
    <td class="tg-hxgm">0.0294</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-1.7</td>
    <td class="tg-5aeg">0.0446</td>
    <td class="tg-5aeg">0.0436</td>
    <td class="tg-5aeg">0.0427</td>
    <td class="tg-5aeg">0.0418</td>
    <td class="tg-5aeg">0.0409</td>
    <td class="tg-5aeg">0.0401</td>
    <td class="tg-5aeg">0.0392</td>
    <td class="tg-5aeg">0.0384</td>
    <td class="tg-5aeg">0.0375</td>
    <td class="tg-5aeg">0.0367</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-1.6</td>
    <td class="tg-hxgm">0.0548</td>
    <td class="tg-hxgm">0.0537</td>
    <td class="tg-hxgm">0.0526</td>
    <td class="tg-hxgm">0.0516</td>
    <td class="tg-hxgm">0.0505</td>
    <td class="tg-hxgm">0.0495</td>
    <td class="tg-hxgm">0.0485</td>
    <td class="tg-hxgm">0.0475</td>
    <td class="tg-hxgm">0.0465</td>
    <td class="tg-hxgm">0.0455</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-1.5</td>
    <td class="tg-5aeg">0.0668</td>
    <td class="tg-5aeg">0.0655</td>
    <td class="tg-5aeg">0.0643</td>
    <td class="tg-5aeg">0.0630</td>
    <td class="tg-5aeg">0.0618</td>
    <td class="tg-5aeg">0.0606</td>
    <td class="tg-5aeg">0.0594</td>
    <td class="tg-5aeg">0.0582</td>
    <td class="tg-5aeg">0.0571</td>
    <td class="tg-5aeg">0.0559</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-1.4</td>
    <td class="tg-hxgm">0.0808</td>
    <td class="tg-hxgm">0.0793</td>
    <td class="tg-hxgm">0.0778</td>
    <td class="tg-hxgm">0.0764</td>
    <td class="tg-hxgm">0.0749</td>
    <td class="tg-hxgm">0.0735</td>
    <td class="tg-hxgm">0.0721</td>
    <td class="tg-hxgm">0.0708</td>
    <td class="tg-hxgm">0.0694</td>
    <td class="tg-hxgm">0.0681</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-1.3</td>
    <td class="tg-5aeg">0.0968</td>
    <td class="tg-5aeg">0.0951</td>
    <td class="tg-5aeg">0.0934</td>
    <td class="tg-5aeg">0.0918</td>
    <td class="tg-5aeg">0.0901</td>
    <td class="tg-5aeg">0.0885</td>
    <td class="tg-5aeg">0.0869</td>
    <td class="tg-5aeg">0.0853</td>
    <td class="tg-5aeg">0.0838</td>
    <td class="tg-5aeg">0.0823</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-1.2</td>
    <td class="tg-hxgm">0.1151</td>
    <td class="tg-hxgm">0.1131</td>
    <td class="tg-hxgm">0.1112</td>
    <td class="tg-hxgm">0.1093</td>
    <td class="tg-hxgm">0.1075</td>
    <td class="tg-hxgm">0.1056</td>
    <td class="tg-hxgm">0.1038</td>
    <td class="tg-hxgm">0.1020</td>
    <td class="tg-hxgm">0.1003</td>
    <td class="tg-hxgm">0.0985</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-1.1</td>
    <td class="tg-5aeg">0.1357</td>
    <td class="tg-5aeg">0.1335</td>
    <td class="tg-5aeg">0.1314</td>
    <td class="tg-5aeg">0.1292</td>
    <td class="tg-5aeg">0.1271</td>
    <td class="tg-5aeg">0.1251</td>
    <td class="tg-5aeg">0.1230</td>
    <td class="tg-5aeg">0.1210</td>
    <td class="tg-5aeg">0.1190</td>
    <td class="tg-5aeg">0.1170</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-1.0</td>
    <td class="tg-hxgm">0.1587</td>
    <td class="tg-hxgm">0.1562</td>
    <td class="tg-hxgm">0.1539</td>
    <td class="tg-hxgm">0.1515</td>
    <td class="tg-hxgm">0.1492</td>
    <td class="tg-hxgm">0.1469</td>
    <td class="tg-hxgm">0.1446</td>
    <td class="tg-hxgm">0.1423</td>
    <td class="tg-hxgm">0.1401</td>
    <td class="tg-hxgm">0.1379</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-0.9</td>
    <td class="tg-5aeg">0.1841</td>
    <td class="tg-5aeg">0.1814</td>
    <td class="tg-5aeg">0.1788</td>
    <td class="tg-5aeg">0.1762</td>
    <td class="tg-5aeg">0.1736</td>
    <td class="tg-5aeg">0.1711</td>
    <td class="tg-5aeg">0.1685</td>
    <td class="tg-5aeg">0.1660</td>
    <td class="tg-5aeg">0.1635</td>
    <td class="tg-5aeg">0.1611</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-0.8</td>
    <td class="tg-hxgm">0.2119</td>
    <td class="tg-hxgm">0.2090</td>
    <td class="tg-hxgm">0.2061</td>
    <td class="tg-hxgm">0.2033</td>
    <td class="tg-hxgm">0.2005</td>
    <td class="tg-hxgm">0.1977</td>
    <td class="tg-hxgm">0.1949</td>
    <td class="tg-hxgm">0.1922</td>
    <td class="tg-hxgm">0.1894</td>
    <td class="tg-hxgm">0.1867</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-0.7</td>
    <td class="tg-5aeg">0.2420</td>
    <td class="tg-5aeg">0.2389</td>
    <td class="tg-5aeg">0.2358</td>
    <td class="tg-5aeg">0.2327</td>
    <td class="tg-5aeg">0.2296</td>
    <td class="tg-5aeg">0.2266</td>
    <td class="tg-5aeg">0.2236</td>
    <td class="tg-5aeg">0.2206</td>
    <td class="tg-5aeg">0.2177</td>
    <td class="tg-5aeg">0.2148</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-0.6</td>
    <td class="tg-hxgm">0.2743</td>
    <td class="tg-hxgm">0.2709</td>
    <td class="tg-hxgm">0.2676</td>
    <td class="tg-hxgm">0.2643</td>
    <td class="tg-hxgm">0.2611</td>
    <td class="tg-hxgm">0.2578</td>
    <td class="tg-hxgm">0.2546</td>
    <td class="tg-hxgm">0.2514</td>
    <td class="tg-hxgm">0.2483</td>
    <td class="tg-hxgm">0.2451</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-0.5</td>
    <td class="tg-5aeg">0.3085</td>
    <td class="tg-5aeg">0.305</td>
    <td class="tg-5aeg">0.3015</td>
    <td class="tg-5aeg">0.2981</td>
    <td class="tg-5aeg">0.2946</td>
    <td class="tg-5aeg">0.2912</td>
    <td class="tg-5aeg">0.2877</td>
    <td class="tg-5aeg">0.2843</td>
    <td class="tg-5aeg">0.281</td>
    <td class="tg-5aeg">0.2776</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-0.4</td>
    <td class="tg-hxgm">0.3446</td>
    <td class="tg-hxgm">0.3409</td>
    <td class="tg-hxgm">0.3372</td>
    <td class="tg-hxgm">0.3336</td>
    <td class="tg-hxgm">0.3300</td>
    <td class="tg-hxgm">0.3264</td>
    <td class="tg-hxgm">0.3228</td>
    <td class="tg-hxgm">0.3192</td>
    <td class="tg-hxgm">0.3156</td>
    <td class="tg-hxgm">0.3121</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-0.3</td>
    <td class="tg-5aeg">0.3821</td>
    <td class="tg-5aeg">0.3783</td>
    <td class="tg-5aeg">0.3745</td>
    <td class="tg-5aeg">0.3707</td>
    <td class="tg-5aeg">0.3669</td>
    <td class="tg-5aeg">0.3632</td>
    <td class="tg-5aeg">0.3594</td>
    <td class="tg-5aeg">0.3557</td>
    <td class="tg-5aeg">0.3520</td>
    <td class="tg-5aeg">0.3483</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-0.2</td>
    <td class="tg-hxgm">0.4207</td>
    <td class="tg-hxgm">0.4168</td>
    <td class="tg-hxgm">0.4129</td>
    <td class="tg-hxgm">0.4090</td>
    <td class="tg-hxgm">0.4052</td>
    <td class="tg-hxgm">0.4013</td>
    <td class="tg-hxgm">0.3974</td>
    <td class="tg-hxgm">0.3936</td>
    <td class="tg-hxgm">0.3897</td>
    <td class="tg-hxgm">0.3859</td>
  </tr>
  <tr>
    <td class="tg-fb3z">-0.1</td>
    <td class="tg-5aeg">0.4602</td>
    <td class="tg-5aeg">0.4562</td>
    <td class="tg-5aeg">0.4522</td>
    <td class="tg-5aeg">0.4483</td>
    <td class="tg-5aeg">0.4443</td>
    <td class="tg-5aeg">0.4404</td>
    <td class="tg-5aeg">0.4364</td>
    <td class="tg-5aeg">0.4325</td>
    <td class="tg-5aeg">0.4286</td>
    <td class="tg-5aeg">0.4247</td>
  </tr>
  <tr>
    <td class="tg-fb3z">0.0</td>
    <td class="tg-hxgm">0.5000</td>
    <td class="tg-hxgm">0.4960</td>
    <td class="tg-hxgm">0.4920</td>
    <td class="tg-hxgm">0.4880</td>
    <td class="tg-hxgm">0.4840</td>
    <td class="tg-hxgm">0.4801</td>
    <td class="tg-hxgm">0.4761</td>
    <td class="tg-hxgm">0.4721</td>
    <td class="tg-hxgm">0.4681</td>
    <td class="tg-hxgm">0.4641</td>
  </tr>
</tbody>
</table>

</details>

```{r standard normal dist table cont, echo = FALSE}
ggplot() +
    geom_polygon(aes(x = c(-4, seq(-4,1,0.01), 1), y = c(0, dnorm(seq(-4,1,0.01)), 0)), alpha = 0.5) +
    stat_function(fun = dnorm, xlim = c(-4, 4), size = 1.2, n = 1000) + theme_void() +
    annotate("segment", x = 1, xend = 1, y = -.01, yend = .01, size = 1.1) + 
    annotate("text", x = 1, y = -.025, label = "z") +
    annotate("segment", x = -2.3, y = .3, xend = -.1, yend = .2, arrow = arrow(), size = 1.1) +
    annotate("text", x = -3.2, y = 0.3, label =  "Probability p")

# x.2 <- seq(-4,1,0.01)
# par(mar=c(3,1,1,1))
# plot.new()
# plot.window(c(-4, 4), c(0, .4))
# lines(x, dnorm(x), lwd = 1.5)
# polygon(c(x.2, x.2[length(x.2)]), c(dnorm(x.2), 0), col = "gray")
# axis(side = 1, at = 1, labels = expression(z))
# arrows(-2.5, .3, -.1, .2, lwd = 1.5)
# text(-3.2, .3, "Probability")
# box()
```

<details>
  <summary> Click for table of standard normal probabilities (continued) </summary>

Table entry for $z$ is the probability lying below $z$.

<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;width:100%;}
.tg td{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  overflow:hidden;padding:10px 5px;word-break:normal;}
.tg th{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-5aeg{background-color:#C0C0C0;border-color:#000000;font-family:"Lucida Console", Monaco, monospace !important;
  text-align:center;vertical-align:bottom}
.tg .tg-fb3z{background-color:#343434;border-color:#000000;color:#FFF;font-family:"Lucida Console", Monaco, monospace !important;
  font-weight:bold;text-align:center;vertical-align:bottom}
.tg .tg-hxgm{border-color:#000000;font-family:"Lucida Console", Monaco, monospace !important;text-align:center;vertical-align:bottom
  }
</style>

<table class="tg">
<thead>
  <tr>
    <th class="tg-fb3z">$z$</th>
    <th class="tg-fb3z">0.00</th>
    <th class="tg-fb3z">0.01</th>
    <th class="tg-fb3z">0.02</th>
    <th class="tg-fb3z">0.03</th>
    <th class="tg-fb3z">0.04</th>
    <th class="tg-fb3z">0.05</th>
    <th class="tg-fb3z">0.06</th>
    <th class="tg-fb3z">0.07</th>
    <th class="tg-fb3z">0.08</th>
    <th class="tg-fb3z">0.09</th>
  </tr>
</thead>
<tbody>
  <tr>
    <td class="tg-fb3z">0.0</td>
    <td class="tg-hxgm">0.5000</td>
    <td class="tg-hxgm">0.5040</td>
    <td class="tg-hxgm">0.5080</td>
    <td class="tg-hxgm">0.5120</td>
    <td class="tg-hxgm">0.5160</td>
    <td class="tg-hxgm">0.5199</td>
    <td class="tg-hxgm">0.5239</td>
    <td class="tg-hxgm">0.5279</td>
    <td class="tg-hxgm">0.5319</td>
    <td class="tg-hxgm">0.5359</td>
  </tr>
  <tr>
    <td class="tg-fb3z">0.1</td>
    <td class="tg-5aeg">0.5398</td>
    <td class="tg-5aeg">0.5438</td>
    <td class="tg-5aeg">0.5478</td>
    <td class="tg-5aeg">0.5517</td>
    <td class="tg-5aeg">0.5557</td>
    <td class="tg-5aeg">0.5596</td>
    <td class="tg-5aeg">0.5636</td>
    <td class="tg-5aeg">0.5675</td>
    <td class="tg-5aeg">0.5714</td>
    <td class="tg-5aeg">0.5753</td>
  </tr>
  <tr>
    <td class="tg-fb3z">0.2</td>
    <td class="tg-hxgm">0.5793</td>
    <td class="tg-hxgm">0.5832</td>
    <td class="tg-hxgm">0.5871</td>
    <td class="tg-hxgm">0.5910</td>
    <td class="tg-hxgm">0.5948</td>
    <td class="tg-hxgm">0.5987</td>
    <td class="tg-hxgm">0.6026</td>
    <td class="tg-hxgm">0.6064</td>
    <td class="tg-hxgm">0.6103</td>
    <td class="tg-hxgm">0.6141</td>
  </tr>
  <tr>
    <td class="tg-fb3z">0.3</td>
    <td class="tg-5aeg">0.6179</td>
    <td class="tg-5aeg">0.6217</td>
    <td class="tg-5aeg">0.6255</td>
    <td class="tg-5aeg">0.6293</td>
    <td class="tg-5aeg">0.6331</td>
    <td class="tg-5aeg">0.6368</td>
    <td class="tg-5aeg">0.6406</td>
    <td class="tg-5aeg">0.6443</td>
    <td class="tg-5aeg">0.6480</td>
    <td class="tg-5aeg">0.6517</td>
  </tr>
  <tr>
    <td class="tg-fb3z">0.4</td>
    <td class="tg-hxgm">0.6554</td>
    <td class="tg-hxgm">0.6591</td>
    <td class="tg-hxgm">0.6628</td>
    <td class="tg-hxgm">0.6664</td>
    <td class="tg-hxgm">0.6700</td>
    <td class="tg-hxgm">0.6736</td>
    <td class="tg-hxgm">0.6772</td>
    <td class="tg-hxgm">0.6808</td>
    <td class="tg-hxgm">0.6844</td>
    <td class="tg-hxgm">0.6879</td>
  </tr>
  <tr>
    <td class="tg-fb3z">0.5</td>
    <td class="tg-5aeg">0.6915</td>
    <td class="tg-5aeg">0.6950</td>
    <td class="tg-5aeg">0.6985</td>
    <td class="tg-5aeg">0.7019</td>
    <td class="tg-5aeg">0.7054</td>
    <td class="tg-5aeg">0.7088</td>
    <td class="tg-5aeg">0.7123</td>
    <td class="tg-5aeg">0.7157</td>
    <td class="tg-5aeg">0.7190</td>
    <td class="tg-5aeg">0.7224</td>
  </tr>
  <tr>
    <td class="tg-fb3z">0.6</td>
    <td class="tg-hxgm">0.7257</td>
    <td class="tg-hxgm">0.7291</td>
    <td class="tg-hxgm">0.7324</td>
    <td class="tg-hxgm">0.7357</td>
    <td class="tg-hxgm">0.7389</td>
    <td class="tg-hxgm">0.7422</td>
    <td class="tg-hxgm">0.7454</td>
    <td class="tg-hxgm">0.7486</td>
    <td class="tg-hxgm">0.7517</td>
    <td class="tg-hxgm">0.7549</td>
  </tr>
  <tr>
    <td class="tg-fb3z">0.7</td>
    <td class="tg-5aeg">0.7580</td>
    <td class="tg-5aeg">0.7611</td>
    <td class="tg-5aeg">0.7642</td>
    <td class="tg-5aeg">0.7673</td>
    <td class="tg-5aeg">0.7704</td>
    <td class="tg-5aeg">0.7734</td>
    <td class="tg-5aeg">0.7764</td>
    <td class="tg-5aeg">0.7794</td>
    <td class="tg-5aeg">0.7823</td>
    <td class="tg-5aeg">0.7852</td>
  </tr>
  <tr>
    <td class="tg-fb3z">0.8</td>
    <td class="tg-hxgm">0.7881</td>
    <td class="tg-hxgm">0.7910</td>
    <td class="tg-hxgm">0.7939</td>
    <td class="tg-hxgm">0.7967</td>
    <td class="tg-hxgm">0.7995</td>
    <td class="tg-hxgm">0.8023</td>
    <td class="tg-hxgm">0.8051</td>
    <td class="tg-hxgm">0.8078</td>
    <td class="tg-hxgm">0.8106</td>
    <td class="tg-hxgm">0.8133</td>
  </tr>
  <tr>
    <td class="tg-fb3z">0.9</td>
    <td class="tg-5aeg">0.8159</td>
    <td class="tg-5aeg">0.8186</td>
    <td class="tg-5aeg">0.8212</td>
    <td class="tg-5aeg">0.8238</td>
    <td class="tg-5aeg">0.8264</td>
    <td class="tg-5aeg">0.8289</td>
    <td class="tg-5aeg">0.8315</td>
    <td class="tg-5aeg">0.8340</td>
    <td class="tg-5aeg">0.8365</td>
    <td class="tg-5aeg">0.8389</td>
  </tr>
  <tr>
    <td class="tg-fb3z">1.0</td>
    <td class="tg-hxgm">0.8413</td>
    <td class="tg-hxgm">0.8438</td>
    <td class="tg-hxgm">0.8461</td>
    <td class="tg-hxgm">0.8485</td>
    <td class="tg-hxgm">0.8508</td>
    <td class="tg-hxgm">0.8531</td>
    <td class="tg-hxgm">0.8554</td>
    <td class="tg-hxgm">0.8577</td>
    <td class="tg-hxgm">0.8599</td>
    <td class="tg-hxgm">0.8621</td>
  </tr>
  <tr>
    <td class="tg-fb3z">1.1</td>
    <td class="tg-5aeg">0.8643</td>
    <td class="tg-5aeg">0.8665</td>
    <td class="tg-5aeg">0.8686</td>
    <td class="tg-5aeg">0.8708</td>
    <td class="tg-5aeg">0.8729</td>
    <td class="tg-5aeg">0.8749</td>
    <td class="tg-5aeg">0.8770</td>
    <td class="tg-5aeg">0.8790</td>
    <td class="tg-5aeg">0.8810</td>
    <td class="tg-5aeg">0.8830</td>
  </tr>
  <tr>
    <td class="tg-fb3z">1.2</td>
    <td class="tg-hxgm">0.8849</td>
    <td class="tg-hxgm">0.8869</td>
    <td class="tg-hxgm">0.8888</td>
    <td class="tg-hxgm">0.8907</td>
    <td class="tg-hxgm">0.8925</td>
    <td class="tg-hxgm">0.8944</td>
    <td class="tg-hxgm">0.8962</td>
    <td class="tg-hxgm">0.8980</td>
    <td class="tg-hxgm">0.8997</td>
    <td class="tg-hxgm">0.9015</td>
  </tr>
  <tr>
    <td class="tg-fb3z">1.3</td>
    <td class="tg-5aeg">0.9032</td>
    <td class="tg-5aeg">0.9049</td>
    <td class="tg-5aeg">0.9066</td>
    <td class="tg-5aeg">0.9082</td>
    <td class="tg-5aeg">0.9099</td>
    <td class="tg-5aeg">0.9115</td>
    <td class="tg-5aeg">0.9131</td>
    <td class="tg-5aeg">0.9147</td>
    <td class="tg-5aeg">0.9162</td>
    <td class="tg-5aeg">0.9177</td>
  </tr>
  <tr>
    <td class="tg-fb3z">1.4</td>
    <td class="tg-hxgm">0.9192</td>
    <td class="tg-hxgm">0.9207</td>
    <td class="tg-hxgm">0.9222</td>
    <td class="tg-hxgm">0.9236</td>
    <td class="tg-hxgm">0.9251</td>
    <td class="tg-hxgm">0.9265</td>
    <td class="tg-hxgm">0.9279</td>
    <td class="tg-hxgm">0.9292</td>
    <td class="tg-hxgm">0.9306</td>
    <td class="tg-hxgm">0.9319</td>
  </tr>
  <tr>
    <td class="tg-fb3z">1.5</td>
    <td class="tg-5aeg">0.9332</td>
    <td class="tg-5aeg">0.9345</td>
    <td class="tg-5aeg">0.9357</td>
    <td class="tg-5aeg">0.9370</td>
    <td class="tg-5aeg">0.9382</td>
    <td class="tg-5aeg">0.9394</td>
    <td class="tg-5aeg">0.9406</td>
    <td class="tg-5aeg">0.9418</td>
    <td class="tg-5aeg">0.9429</td>
    <td class="tg-5aeg">0.9441</td>
  </tr>
  <tr>
    <td class="tg-fb3z">1.6</td>
    <td class="tg-hxgm">0.9452</td>
    <td class="tg-hxgm">0.9463</td>
    <td class="tg-hxgm">0.9474</td>
    <td class="tg-hxgm">0.9484</td>
    <td class="tg-hxgm">0.9495</td>
    <td class="tg-hxgm">0.9505</td>
    <td class="tg-hxgm">0.9515</td>
    <td class="tg-hxgm">0.9525</td>
    <td class="tg-hxgm">0.9535</td>
    <td class="tg-hxgm">0.9545</td>
  </tr>
  <tr>
    <td class="tg-fb3z">1.7</td>
    <td class="tg-5aeg">0.9554</td>
    <td class="tg-5aeg">0.9564</td>
    <td class="tg-5aeg">0.9573</td>
    <td class="tg-5aeg">0.9582</td>
    <td class="tg-5aeg">0.9591</td>
    <td class="tg-5aeg">0.9599</td>
    <td class="tg-5aeg">0.9608</td>
    <td class="tg-5aeg">0.9616</td>
    <td class="tg-5aeg">0.9625</td>
    <td class="tg-5aeg">0.9633</td>
  </tr>
  <tr>
    <td class="tg-fb3z">1.8</td>
    <td class="tg-hxgm">0.9641</td>
    <td class="tg-hxgm">0.9649</td>
    <td class="tg-hxgm">0.9656</td>
    <td class="tg-hxgm">0.9664</td>
    <td class="tg-hxgm">0.9671</td>
    <td class="tg-hxgm">0.9678</td>
    <td class="tg-hxgm">0.9686</td>
    <td class="tg-hxgm">0.9693</td>
    <td class="tg-hxgm">0.9699</td>
    <td class="tg-hxgm">0.9706</td>
  </tr>
  <tr>
    <td class="tg-fb3z">1.9</td>
    <td class="tg-5aeg">0.9713</td>
    <td class="tg-5aeg">0.9719</td>
    <td class="tg-5aeg">0.9726</td>
    <td class="tg-5aeg">0.9732</td>
    <td class="tg-5aeg">0.9738</td>
    <td class="tg-5aeg">0.9744</td>
    <td class="tg-5aeg">0.9750</td>
    <td class="tg-5aeg">0.9756</td>
    <td class="tg-5aeg">0.9761</td>
    <td class="tg-5aeg">0.9767</td>
  </tr>
  <tr>
    <td class="tg-fb3z">2.0</td>
    <td class="tg-hxgm">0.9772</td>
    <td class="tg-hxgm">0.9778</td>
    <td class="tg-hxgm">0.9783</td>
    <td class="tg-hxgm">0.9788</td>
    <td class="tg-hxgm">0.9793</td>
    <td class="tg-hxgm">0.9798</td>
    <td class="tg-hxgm">0.9803</td>
    <td class="tg-hxgm">0.9808</td>
    <td class="tg-hxgm">0.9812</td>
    <td class="tg-hxgm">0.9817</td>
  </tr>
  <tr>
    <td class="tg-fb3z">2.1</td>
    <td class="tg-5aeg">0.9821</td>
    <td class="tg-5aeg">0.9826</td>
    <td class="tg-5aeg">0.9830</td>
    <td class="tg-5aeg">0.9834</td>
    <td class="tg-5aeg">0.9838</td>
    <td class="tg-5aeg">0.9842</td>
    <td class="tg-5aeg">0.9846</td>
    <td class="tg-5aeg">0.9850</td>
    <td class="tg-5aeg">0.9854</td>
    <td class="tg-5aeg">0.9857</td>
  </tr>
  <tr>
    <td class="tg-fb3z">2.2</td>
    <td class="tg-hxgm">0.9861</td>
    <td class="tg-hxgm">0.9864</td>
    <td class="tg-hxgm">0.9868</td>
    <td class="tg-hxgm">0.9871</td>
    <td class="tg-hxgm">0.9875</td>
    <td class="tg-hxgm">0.9878</td>
    <td class="tg-hxgm">0.9881</td>
    <td class="tg-hxgm">0.9884</td>
    <td class="tg-hxgm">0.9887</td>
    <td class="tg-hxgm">0.9890</td>
  </tr>
  <tr>
    <td class="tg-fb3z">2.3</td>
    <td class="tg-5aeg">0.9893</td>
    <td class="tg-5aeg">0.9896</td>
    <td class="tg-5aeg">0.9898</td>
    <td class="tg-5aeg">0.9901</td>
    <td class="tg-5aeg">0.9904</td>
    <td class="tg-5aeg">0.9906</td>
    <td class="tg-5aeg">0.9909</td>
    <td class="tg-5aeg">0.9911</td>
    <td class="tg-5aeg">0.9913</td>
    <td class="tg-5aeg">0.9916</td>
  </tr>
  <tr>
    <td class="tg-fb3z">2.4</td>
    <td class="tg-hxgm">0.9918</td>
    <td class="tg-hxgm">0.9920</td>
    <td class="tg-hxgm">0.9922</td>
    <td class="tg-hxgm">0.9925</td>
    <td class="tg-hxgm">0.9927</td>
    <td class="tg-hxgm">0.9929</td>
    <td class="tg-hxgm">0.9931</td>
    <td class="tg-hxgm">0.9932</td>
    <td class="tg-hxgm">0.9934</td>
    <td class="tg-hxgm">0.9936</td>
  </tr>
  <tr>
    <td class="tg-fb3z">2.5</td>
    <td class="tg-5aeg">0.9938</td>
    <td class="tg-5aeg">0.9940</td>
    <td class="tg-5aeg">0.9941</td>
    <td class="tg-5aeg">0.9943</td>
    <td class="tg-5aeg">0.9945</td>
    <td class="tg-5aeg">0.9946</td>
    <td class="tg-5aeg">0.9948</td>
    <td class="tg-5aeg">0.9949</td>
    <td class="tg-5aeg">0.9951</td>
    <td class="tg-5aeg">0.9952</td>
  </tr>
  <tr>
    <td class="tg-fb3z">2.6</td>
    <td class="tg-hxgm">0.9953</td>
    <td class="tg-hxgm">0.9955</td>
    <td class="tg-hxgm">0.9956</td>
    <td class="tg-hxgm">0.9957</td>
    <td class="tg-hxgm">0.9959</td>
    <td class="tg-hxgm">0.9960</td>
    <td class="tg-hxgm">0.9961</td>
    <td class="tg-hxgm">0.9962</td>
    <td class="tg-hxgm">0.9963</td>
    <td class="tg-hxgm">0.9964</td>
  </tr>
  <tr>
    <td class="tg-fb3z">2.7</td>
    <td class="tg-5aeg">0.9965</td>
    <td class="tg-5aeg">0.9966</td>
    <td class="tg-5aeg">0.9967</td>
    <td class="tg-5aeg">0.9968</td>
    <td class="tg-5aeg">0.9969</td>
    <td class="tg-5aeg">0.9970</td>
    <td class="tg-5aeg">0.9971</td>
    <td class="tg-5aeg">0.9972</td>
    <td class="tg-5aeg">0.9973</td>
    <td class="tg-5aeg">0.9974</td>
  </tr>
  <tr>
    <td class="tg-fb3z">2.8</td>
    <td class="tg-hxgm">0.9974</td>
    <td class="tg-hxgm">0.9975</td>
    <td class="tg-hxgm">0.9976</td>
    <td class="tg-hxgm">0.9977</td>
    <td class="tg-hxgm">0.9977</td>
    <td class="tg-hxgm">0.9978</td>
    <td class="tg-hxgm">0.9979</td>
    <td class="tg-hxgm">0.9979</td>
    <td class="tg-hxgm">0.9980</td>
    <td class="tg-hxgm">0.9981</td>
  </tr>
  <tr>
    <td class="tg-fb3z">2.9</td>
    <td class="tg-5aeg">0.9981</td>
    <td class="tg-5aeg">0.9982</td>
    <td class="tg-5aeg">0.9982</td>
    <td class="tg-5aeg">0.9983</td>
    <td class="tg-5aeg">0.9984</td>
    <td class="tg-5aeg">0.9984</td>
    <td class="tg-5aeg">0.9985</td>
    <td class="tg-5aeg">0.9985</td>
    <td class="tg-5aeg">0.9986</td>
    <td class="tg-5aeg">0.9986</td>
  </tr>
  <tr>
    <td class="tg-fb3z">3.0</td>
    <td class="tg-hxgm">0.9987</td>
    <td class="tg-hxgm">0.9987</td>
    <td class="tg-hxgm">0.9987</td>
    <td class="tg-hxgm">0.9988</td>
    <td class="tg-hxgm">0.9988</td>
    <td class="tg-hxgm">0.9989</td>
    <td class="tg-hxgm">0.9989</td>
    <td class="tg-hxgm">0.9989</td>
    <td class="tg-hxgm">0.9990</td>
    <td class="tg-hxgm">0.9990</td>
  </tr>
  <tr>
    <td class="tg-fb3z">3.1</td>
    <td class="tg-5aeg">0.9990</td>
    <td class="tg-5aeg">0.9991</td>
    <td class="tg-5aeg">0.9991</td>
    <td class="tg-5aeg">0.9991</td>
    <td class="tg-5aeg">0.9992</td>
    <td class="tg-5aeg">0.9992</td>
    <td class="tg-5aeg">0.9992</td>
    <td class="tg-5aeg">0.9992</td>
    <td class="tg-5aeg">0.9993</td>
    <td class="tg-5aeg">0.9993</td>
  </tr>
  <tr>
    <td class="tg-fb3z">3.2</td>
    <td class="tg-hxgm">0.9993</td>
    <td class="tg-hxgm">0.9993</td>
    <td class="tg-hxgm">0.9994</td>
    <td class="tg-hxgm">0.9994</td>
    <td class="tg-hxgm">0.9994</td>
    <td class="tg-hxgm">0.9994</td>
    <td class="tg-hxgm">0.9994</td>
    <td class="tg-hxgm">0.9995</td>
    <td class="tg-hxgm">0.9995</td>
    <td class="tg-hxgm">0.9995</td>
  </tr>
  <tr>
    <td class="tg-fb3z">3.3</td>
    <td class="tg-5aeg">0.9995</td>
    <td class="tg-5aeg">0.9995</td>
    <td class="tg-5aeg">0.9995</td>
    <td class="tg-5aeg">0.9996</td>
    <td class="tg-5aeg">0.9996</td>
    <td class="tg-5aeg">0.9996</td>
    <td class="tg-5aeg">0.9996</td>
    <td class="tg-5aeg">0.9996</td>
    <td class="tg-5aeg">0.9996</td>
    <td class="tg-5aeg">0.9997</td>
  </tr>
  <tr>
    <td class="tg-fb3z">3.4</td>
    <td class="tg-hxgm">0.9997</td>
    <td class="tg-hxgm">0.9997</td>
    <td class="tg-hxgm">0.9997</td>
    <td class="tg-hxgm">0.9997</td>
    <td class="tg-hxgm">0.9997</td>
    <td class="tg-hxgm">0.9997</td>
    <td class="tg-hxgm">0.9997</td>
    <td class="tg-hxgm">0.9997</td>
    <td class="tg-hxgm">0.9997</td>
    <td class="tg-hxgm">0.9998</td>
  </tr>
</tbody>
</table>

</details>

## Table B: $t$ distribution critical values {#table-b}

```{r t dist table, echo = FALSE}
ggplot() +
    geom_polygon(aes(x = c(1, seq(1,4,0.01), 4), y = c(0, dnorm(seq(1,4,0.01)), 0)), alpha = 0.5) +
    stat_function(fun = dnorm, xlim = c(-4, 4), size = 1.2, n = 1000) + theme_void() +
    annotate("segment", x = 1, xend = 1, y = -.01, yend = .01, size = 1.1) + 
    annotate("text", x = 1, y = -.025, label = "t") +
    annotate("segment", x = 3, y = .15, xend = 1.5, yend = .05, arrow = arrow(), size = 1.5) +
    annotate("text", x = 3, y = 0.17, label =  "Probability p")

# x.3 <- seq(1,4,0.01)
# par(mar = c(3,1,1,1))
# plot.new()
# plot.window(c(-4, 4), c(0, .4))
# lines(x, dnorm(x), lwd = 1.5)
# polygon(c(1, x.3), c(0, dnorm(x.3)), col = "gray")
# axis(side = 1, at = 1, labels = "t*")
# arrows(3, .15, 1.5, .05, lwd = 1.5)
# text(3, .17, "Probability p")
# box()
```

```{r t dist table calc, echo = FALSE}
# dfs <- c(1:30, 40, 50, 60, 80, 100, 1000, Inf)
# ps <- c(.25, .2, .15, .1, .05, .025, .02, .01, .005, .0025, .001, .0005)
# 
# t_vals_df = data.frame(replicate(12, numeric(37)))
# 
# rownames(t_vals_df) <- dfs
# colnames(t_vals_df) <- ps
# 
# for (p in ps) {
#     t_vals_df[[paste(p)]] <- qt(p, dfs, lower.tail = FALSE)
# }
# 
# write.csv(t_vals_df, "t_vals_df.csv")
```
<details>
  <summary> Click here for table of $t$ distribution critical values </summary>

Table entry for $p$ and $C$ is the point $t*$ with probability $p$ lying above it and probability $C$ lying between $-t*$ and $t*$.

<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;}
.tg td{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  overflow:hidden;padding:10px 5px;word-break:normal;}
.tg th{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-qw8e{background-color:#c0c0c0;border-color:#000000;font-family:"Lucida Console", Monaco, monospace !important;
  text-align:center;vertical-align:top}
.tg .tg-8qbv{background-color:#ffffff;border-color:#000000;color:#000000;font-family:"Lucida Console", Monaco, monospace !important;
  text-align:center;vertical-align:bottom}
.tg .tg-hp4q{background-color:#ffffff;border-color:#000000;color:#ffffff;font-family:"Lucida Console", Monaco, monospace !important;
  font-weight:bold;text-align:center;vertical-align:top}
.tg .tg-g5p5{background-color:#ffffff;border-color:#000000;font-family:"Lucida Console", Monaco, monospace !important;
  text-align:center;vertical-align:top}
.tg .tg-oaw3{background-color:#343434;border-color:#000000;color:#ffffff;font-family:"Lucida Console", Monaco, monospace !important;
  font-weight:bold;text-align:center;vertical-align:top}
.tg .tg-1lb8{border-color:#000000;font-family:"Lucida Console", Monaco, monospace !important;text-align:center;vertical-align:top}
</style>
<table class="tg">
<thead>
  <tr>
    <th class="tg-8qbv" rowspan="2">df</th>
    <th class="tg-g5p5" colspan="12">Tail Probability $p$</th>
  </tr>
  <tr>
    <th class="tg-oaw3">0.25</th>
    <th class="tg-oaw3">0.20</th>
    <th class="tg-oaw3">0.15</th>
    <th class="tg-oaw3">0.10</th>
    <th class="tg-oaw3">0.05</th>
    <th class="tg-oaw3">0.025</th>
    <th class="tg-oaw3">0.02</th>
    <th class="tg-oaw3">0.01</th>
    <th class="tg-oaw3">0.005</th>
    <th class="tg-oaw3">0.0025</th>
    <th class="tg-oaw3">0.001</th>
    <th class="tg-oaw3">0.0005</th>
  </tr>
</thead>
<tbody>
  <tr>
    <td class="tg-oaw3">1</td>
    <td class="tg-1lb8">1.000</td>
    <td class="tg-1lb8">1.376</td>
    <td class="tg-1lb8">1.963</td>
    <td class="tg-1lb8">3.078</td>
    <td class="tg-1lb8">6.314</td>
    <td class="tg-1lb8">12.71</td>
    <td class="tg-1lb8">15.89</td>
    <td class="tg-1lb8">31.82</td>
    <td class="tg-1lb8">63.66</td>
    <td class="tg-1lb8">127.3</td>
    <td class="tg-1lb8">318.3</td>
    <td class="tg-1lb8">636.6</td>
  </tr>
  <tr>
    <td class="tg-oaw3">2</td>
    <td class="tg-qw8e">0.816</td>
    <td class="tg-qw8e">1.061</td>
    <td class="tg-qw8e">1.386</td>
    <td class="tg-qw8e">1.886</td>
    <td class="tg-qw8e">2.920</td>
    <td class="tg-qw8e">4.303</td>
    <td class="tg-qw8e">4.849</td>
    <td class="tg-qw8e">6.965</td>
    <td class="tg-qw8e">9.925</td>
    <td class="tg-qw8e">14.09</td>
    <td class="tg-qw8e">22.33</td>
    <td class="tg-qw8e">31.60</td>
  </tr>
  <tr>
    <td class="tg-oaw3">3</td>
    <td class="tg-1lb8">0.765</td>
    <td class="tg-1lb8">0.978</td>
    <td class="tg-1lb8">1.250</td>
    <td class="tg-1lb8">1.638</td>
    <td class="tg-1lb8">2.353</td>
    <td class="tg-1lb8">3.182</td>
    <td class="tg-1lb8">3.482</td>
    <td class="tg-1lb8">4.541</td>
    <td class="tg-1lb8">5.841</td>
    <td class="tg-1lb8">7.453</td>
    <td class="tg-1lb8">10.21</td>
    <td class="tg-1lb8">12.92</td>
  </tr>
  <tr>
    <td class="tg-oaw3">4</td>
    <td class="tg-qw8e">0.741</td>
    <td class="tg-qw8e">0.941</td>
    <td class="tg-qw8e">1.190</td>
    <td class="tg-qw8e">1.533</td>
    <td class="tg-qw8e">2.132</td>
    <td class="tg-qw8e">2.776</td>
    <td class="tg-qw8e">2.999</td>
    <td class="tg-qw8e">3.747</td>
    <td class="tg-qw8e">4.604</td>
    <td class="tg-qw8e">5.598</td>
    <td class="tg-qw8e">7.173</td>
    <td class="tg-qw8e">8.610</td>
  </tr>
  <tr>
    <td class="tg-oaw3">5</td>
    <td class="tg-1lb8">0.727</td>
    <td class="tg-1lb8">0.920</td>
    <td class="tg-1lb8">1.156</td>
    <td class="tg-1lb8">1.476</td>
    <td class="tg-1lb8">2.015</td>
    <td class="tg-1lb8">2.571</td>
    <td class="tg-1lb8">2.757</td>
    <td class="tg-1lb8">3.365</td>
    <td class="tg-1lb8">4.032</td>
    <td class="tg-1lb8">4.773</td>
    <td class="tg-1lb8">5.893</td>
    <td class="tg-1lb8">6.869</td>
  </tr>
  <tr>
    <td class="tg-oaw3">6</td>
    <td class="tg-qw8e">0.718</td>
    <td class="tg-qw8e">0.906</td>
    <td class="tg-qw8e">1.134</td>
    <td class="tg-qw8e">1.440</td>
    <td class="tg-qw8e">1.943</td>
    <td class="tg-qw8e">2.447</td>
    <td class="tg-qw8e">2.612</td>
    <td class="tg-qw8e">3.143</td>
    <td class="tg-qw8e">3.707</td>
    <td class="tg-qw8e">4.317</td>
    <td class="tg-qw8e">5.208</td>
    <td class="tg-qw8e">5.959</td>
  </tr>
  <tr>
    <td class="tg-oaw3">7</td>
    <td class="tg-1lb8">0.711</td>
    <td class="tg-1lb8">0.896</td>
    <td class="tg-1lb8">1.119</td>
    <td class="tg-1lb8">1.415</td>
    <td class="tg-1lb8">1.895</td>
    <td class="tg-1lb8">2.365</td>
    <td class="tg-1lb8">2.517</td>
    <td class="tg-1lb8">2.998</td>
    <td class="tg-1lb8">3.499</td>
    <td class="tg-1lb8">4.029</td>
    <td class="tg-1lb8">4.785</td>
    <td class="tg-1lb8">5.408</td>
  </tr>
  <tr>
    <td class="tg-oaw3">8</td>
    <td class="tg-qw8e">0.706</td>
    <td class="tg-qw8e">0.889</td>
    <td class="tg-qw8e">1.108</td>
    <td class="tg-qw8e">1.397</td>
    <td class="tg-qw8e">1.860</td>
    <td class="tg-qw8e">2.306</td>
    <td class="tg-qw8e">2.449</td>
    <td class="tg-qw8e">2.896</td>
    <td class="tg-qw8e">3.355</td>
    <td class="tg-qw8e">3.833</td>
    <td class="tg-qw8e">4.501</td>
    <td class="tg-qw8e">5.041</td>
  </tr>
  <tr>
    <td class="tg-oaw3">9</td>
    <td class="tg-1lb8">0.703</td>
    <td class="tg-1lb8">0.883</td>
    <td class="tg-1lb8">1.100</td>
    <td class="tg-1lb8">1.383</td>
    <td class="tg-1lb8">1.833</td>
    <td class="tg-1lb8">2.262</td>
    <td class="tg-1lb8">2.398</td>
    <td class="tg-1lb8">2.821</td>
    <td class="tg-1lb8">3.250</td>
    <td class="tg-1lb8">3.690</td>
    <td class="tg-1lb8">4.297</td>
    <td class="tg-1lb8">4.781</td>
  </tr>
  <tr>
    <td class="tg-oaw3">10</td>
    <td class="tg-qw8e">0.700</td>
    <td class="tg-qw8e">0.879</td>
    <td class="tg-qw8e">1.093</td>
    <td class="tg-qw8e">1.372</td>
    <td class="tg-qw8e">1.812</td>
    <td class="tg-qw8e">2.228</td>
    <td class="tg-qw8e">2.359</td>
    <td class="tg-qw8e">2.764</td>
    <td class="tg-qw8e">3.169</td>
    <td class="tg-qw8e">3.581</td>
    <td class="tg-qw8e">4.144</td>
    <td class="tg-qw8e">4.587</td>
  </tr>
  <tr>
    <td class="tg-oaw3">11</td>
    <td class="tg-1lb8">0.697</td>
    <td class="tg-1lb8">0.876</td>
    <td class="tg-1lb8">1.088</td>
    <td class="tg-1lb8">1.363</td>
    <td class="tg-1lb8">1.796</td>
    <td class="tg-1lb8">2.201</td>
    <td class="tg-1lb8">2.328</td>
    <td class="tg-1lb8">2.718</td>
    <td class="tg-1lb8">3.106</td>
    <td class="tg-1lb8">3.497</td>
    <td class="tg-1lb8">4.025</td>
    <td class="tg-1lb8">4.437</td>
  </tr>
  <tr>
    <td class="tg-oaw3">12</td>
    <td class="tg-qw8e">0.695</td>
    <td class="tg-qw8e">0.873</td>
    <td class="tg-qw8e">1.083</td>
    <td class="tg-qw8e">1.356</td>
    <td class="tg-qw8e">1.782</td>
    <td class="tg-qw8e">2.179</td>
    <td class="tg-qw8e">2.303</td>
    <td class="tg-qw8e">2.681</td>
    <td class="tg-qw8e">3.055</td>
    <td class="tg-qw8e">3.428</td>
    <td class="tg-qw8e">3.930</td>
    <td class="tg-qw8e">4.318</td>
  </tr>
  <tr>
    <td class="tg-oaw3">13</td>
    <td class="tg-1lb8">0.694</td>
    <td class="tg-1lb8">0.870</td>
    <td class="tg-1lb8">1.079</td>
    <td class="tg-1lb8">1.350</td>
    <td class="tg-1lb8">1.771</td>
    <td class="tg-1lb8">2.160</td>
    <td class="tg-1lb8">2.282</td>
    <td class="tg-1lb8">2.650</td>
    <td class="tg-1lb8">3.012</td>
    <td class="tg-1lb8">3.372</td>
    <td class="tg-1lb8">3.852</td>
    <td class="tg-1lb8">4.221</td>
  </tr>
  <tr>
    <td class="tg-oaw3">14</td>
    <td class="tg-qw8e">0.692</td>
    <td class="tg-qw8e">0.868</td>
    <td class="tg-qw8e">1.076</td>
    <td class="tg-qw8e">1.345</td>
    <td class="tg-qw8e">1.761</td>
    <td class="tg-qw8e">2.145</td>
    <td class="tg-qw8e">2.264</td>
    <td class="tg-qw8e">2.624</td>
    <td class="tg-qw8e">2.977</td>
    <td class="tg-qw8e">3.326</td>
    <td class="tg-qw8e">3.787</td>
    <td class="tg-qw8e">4.140</td>
  </tr>
  <tr>
    <td class="tg-oaw3">15</td>
    <td class="tg-1lb8">0.691</td>
    <td class="tg-1lb8">0.866</td>
    <td class="tg-1lb8">1.074</td>
    <td class="tg-1lb8">1.341</td>
    <td class="tg-1lb8">1.753</td>
    <td class="tg-1lb8">2.131</td>
    <td class="tg-1lb8">2.249</td>
    <td class="tg-1lb8">2.602</td>
    <td class="tg-1lb8">2.947</td>
    <td class="tg-1lb8">3.286</td>
    <td class="tg-1lb8">3.733</td>
    <td class="tg-1lb8">4.073</td>
  </tr>
  <tr>
    <td class="tg-oaw3">16</td>
    <td class="tg-qw8e">0.690</td>
    <td class="tg-qw8e">0.865</td>
    <td class="tg-qw8e">1.071</td>
    <td class="tg-qw8e">1.337</td>
    <td class="tg-qw8e">1.746</td>
    <td class="tg-qw8e">2.120</td>
    <td class="tg-qw8e">2.235</td>
    <td class="tg-qw8e">2.583</td>
    <td class="tg-qw8e">2.921</td>
    <td class="tg-qw8e">3.252</td>
    <td class="tg-qw8e">3.686</td>
    <td class="tg-qw8e">4.015</td>
  </tr>
  <tr>
    <td class="tg-oaw3">17</td>
    <td class="tg-1lb8">0.689</td>
    <td class="tg-1lb8">0.863</td>
    <td class="tg-1lb8">1.069</td>
    <td class="tg-1lb8">1.333</td>
    <td class="tg-1lb8">1.740</td>
    <td class="tg-1lb8">2.110</td>
    <td class="tg-1lb8">2.224</td>
    <td class="tg-1lb8">2.567</td>
    <td class="tg-1lb8">2.898</td>
    <td class="tg-1lb8">3.222</td>
    <td class="tg-1lb8">3.646</td>
    <td class="tg-1lb8">3.965</td>
  </tr>
  <tr>
    <td class="tg-oaw3">18</td>
    <td class="tg-qw8e">0.688</td>
    <td class="tg-qw8e">0.862</td>
    <td class="tg-qw8e">1.067</td>
    <td class="tg-qw8e">1.330</td>
    <td class="tg-qw8e">1.734</td>
    <td class="tg-qw8e">2.101</td>
    <td class="tg-qw8e">2.214</td>
    <td class="tg-qw8e">2.552</td>
    <td class="tg-qw8e">2.878</td>
    <td class="tg-qw8e">3.197</td>
    <td class="tg-qw8e">3.610</td>
    <td class="tg-qw8e">3.922</td>
  </tr>
  <tr>
    <td class="tg-oaw3">19</td>
    <td class="tg-1lb8">0.688</td>
    <td class="tg-1lb8">0.861</td>
    <td class="tg-1lb8">1.066</td>
    <td class="tg-1lb8">1.328</td>
    <td class="tg-1lb8">1.729</td>
    <td class="tg-1lb8">2.093</td>
    <td class="tg-1lb8">2.205</td>
    <td class="tg-1lb8">2.539</td>
    <td class="tg-1lb8">2.861</td>
    <td class="tg-1lb8">3.174</td>
    <td class="tg-1lb8">3.579</td>
    <td class="tg-1lb8">3.883</td>
  </tr>
  <tr>
    <td class="tg-oaw3">20</td>
    <td class="tg-qw8e">0.687</td>
    <td class="tg-qw8e">0.860</td>
    <td class="tg-qw8e">1.064</td>
    <td class="tg-qw8e">1.325</td>
    <td class="tg-qw8e">1.725</td>
    <td class="tg-qw8e">2.086</td>
    <td class="tg-qw8e">2.197</td>
    <td class="tg-qw8e">2.528</td>
    <td class="tg-qw8e">2.845</td>
    <td class="tg-qw8e">3.153</td>
    <td class="tg-qw8e">3.552</td>
    <td class="tg-qw8e">3.850</td>
  </tr>
  <tr>
    <td class="tg-oaw3">21</td>
    <td class="tg-1lb8">0.686</td>
    <td class="tg-1lb8">0.859</td>
    <td class="tg-1lb8">1.063</td>
    <td class="tg-1lb8">1.323</td>
    <td class="tg-1lb8">1.721</td>
    <td class="tg-1lb8">2.080</td>
    <td class="tg-1lb8">2.189</td>
    <td class="tg-1lb8">2.518</td>
    <td class="tg-1lb8">2.831</td>
    <td class="tg-1lb8">3.135</td>
    <td class="tg-1lb8">3.527</td>
    <td class="tg-1lb8">3.819</td>
  </tr>
  <tr>
    <td class="tg-oaw3">22</td>
    <td class="tg-qw8e">0.686</td>
    <td class="tg-qw8e">0.858</td>
    <td class="tg-qw8e">1.061</td>
    <td class="tg-qw8e">1.321</td>
    <td class="tg-qw8e">1.717</td>
    <td class="tg-qw8e">2.074</td>
    <td class="tg-qw8e">2.183</td>
    <td class="tg-qw8e">2.508</td>
    <td class="tg-qw8e">2.819</td>
    <td class="tg-qw8e">3.119</td>
    <td class="tg-qw8e">3.505</td>
    <td class="tg-qw8e">3.792</td>
  </tr>
  <tr>
    <td class="tg-oaw3">23</td>
    <td class="tg-1lb8">0.685</td>
    <td class="tg-1lb8">0.858</td>
    <td class="tg-1lb8">1.060</td>
    <td class="tg-1lb8">1.319</td>
    <td class="tg-1lb8">1.714</td>
    <td class="tg-1lb8">2.069</td>
    <td class="tg-1lb8">2.177</td>
    <td class="tg-1lb8">2.500</td>
    <td class="tg-1lb8">2.807</td>
    <td class="tg-1lb8">3.104</td>
    <td class="tg-1lb8">3.485</td>
    <td class="tg-1lb8">3.768</td>
  </tr>
  <tr>
    <td class="tg-oaw3">24</td>
    <td class="tg-qw8e">0.685</td>
    <td class="tg-qw8e">0.857</td>
    <td class="tg-qw8e">1.059</td>
    <td class="tg-qw8e">1.318</td>
    <td class="tg-qw8e">1.711</td>
    <td class="tg-qw8e">2.064</td>
    <td class="tg-qw8e">2.172</td>
    <td class="tg-qw8e">2.492</td>
    <td class="tg-qw8e">2.797</td>
    <td class="tg-qw8e">3.091</td>
    <td class="tg-qw8e">3.467</td>
    <td class="tg-qw8e">3.745</td>
  </tr>
  <tr>
    <td class="tg-oaw3">25</td>
    <td class="tg-1lb8">0.684</td>
    <td class="tg-1lb8">0.856</td>
    <td class="tg-1lb8">1.058</td>
    <td class="tg-1lb8">1.316</td>
    <td class="tg-1lb8">1.708</td>
    <td class="tg-1lb8">2.060</td>
    <td class="tg-1lb8">2.167</td>
    <td class="tg-1lb8">2.485</td>
    <td class="tg-1lb8">2.787</td>
    <td class="tg-1lb8">3.078</td>
    <td class="tg-1lb8">3.450</td>
    <td class="tg-1lb8">3.725</td>
  </tr>
  <tr>
    <td class="tg-oaw3">26</td>
    <td class="tg-qw8e">0.684</td>
    <td class="tg-qw8e">0.856</td>
    <td class="tg-qw8e">1.058</td>
    <td class="tg-qw8e">1.315</td>
    <td class="tg-qw8e">1.706</td>
    <td class="tg-qw8e">2.056</td>
    <td class="tg-qw8e">2.162</td>
    <td class="tg-qw8e">2.479</td>
    <td class="tg-qw8e">2.779</td>
    <td class="tg-qw8e">3.067</td>
    <td class="tg-qw8e">3.435</td>
    <td class="tg-qw8e">3.707</td>
  </tr>
  <tr>
    <td class="tg-oaw3">27</td>
    <td class="tg-1lb8">0.684</td>
    <td class="tg-1lb8">0.855</td>
    <td class="tg-1lb8">1.057</td>
    <td class="tg-1lb8">1.314</td>
    <td class="tg-1lb8">1.703</td>
    <td class="tg-1lb8">2.052</td>
    <td class="tg-1lb8">2.158</td>
    <td class="tg-1lb8">2.473</td>
    <td class="tg-1lb8">2.771</td>
    <td class="tg-1lb8">3.057</td>
    <td class="tg-1lb8">3.421</td>
    <td class="tg-1lb8">3.690</td>
  </tr>
  <tr>
    <td class="tg-oaw3">28</td>
    <td class="tg-qw8e">0.683</td>
    <td class="tg-qw8e">0.855</td>
    <td class="tg-qw8e">1.056</td>
    <td class="tg-qw8e">1.313</td>
    <td class="tg-qw8e">1.701</td>
    <td class="tg-qw8e">2.048</td>
    <td class="tg-qw8e">2.154</td>
    <td class="tg-qw8e">2.467</td>
    <td class="tg-qw8e">2.763</td>
    <td class="tg-qw8e">3.047</td>
    <td class="tg-qw8e">3.408</td>
    <td class="tg-qw8e">3.674</td>
  </tr>
  <tr>
    <td class="tg-oaw3">29</td>
    <td class="tg-1lb8">0.683</td>
    <td class="tg-1lb8">0.854</td>
    <td class="tg-1lb8">1.055</td>
    <td class="tg-1lb8">1.311</td>
    <td class="tg-1lb8">1.699</td>
    <td class="tg-1lb8">2.045</td>
    <td class="tg-1lb8">2.150</td>
    <td class="tg-1lb8">2.462</td>
    <td class="tg-1lb8">2.756</td>
    <td class="tg-1lb8">3.038</td>
    <td class="tg-1lb8">3.396</td>
    <td class="tg-1lb8">3.659</td>
  </tr>
  <tr>
    <td class="tg-oaw3">30</td>
    <td class="tg-qw8e">0.683</td>
    <td class="tg-qw8e">0.854</td>
    <td class="tg-qw8e">1.055</td>
    <td class="tg-qw8e">1.310</td>
    <td class="tg-qw8e">1.697</td>
    <td class="tg-qw8e">2.042</td>
    <td class="tg-qw8e">2.147</td>
    <td class="tg-qw8e">2.457</td>
    <td class="tg-qw8e">2.750</td>
    <td class="tg-qw8e">3.030</td>
    <td class="tg-qw8e">3.385</td>
    <td class="tg-qw8e">3.646</td>
  </tr>
  <tr>
    <td class="tg-oaw3">40</td>
    <td class="tg-1lb8">0.681</td>
    <td class="tg-1lb8">0.851</td>
    <td class="tg-1lb8">1.050</td>
    <td class="tg-1lb8">1.303</td>
    <td class="tg-1lb8">1.684</td>
    <td class="tg-1lb8">2.021</td>
    <td class="tg-1lb8">2.123</td>
    <td class="tg-1lb8">2.423</td>
    <td class="tg-1lb8">2.704</td>
    <td class="tg-1lb8">2.971</td>
    <td class="tg-1lb8">3.307</td>
    <td class="tg-1lb8">3.551</td>
  </tr>
  <tr>
    <td class="tg-oaw3">50</td>
    <td class="tg-qw8e">0.679</td>
    <td class="tg-qw8e">0.849</td>
    <td class="tg-qw8e">1.047</td>
    <td class="tg-qw8e">1.299</td>
    <td class="tg-qw8e">1.676</td>
    <td class="tg-qw8e">2.009</td>
    <td class="tg-qw8e">2.109</td>
    <td class="tg-qw8e">2.403</td>
    <td class="tg-qw8e">2.678</td>
    <td class="tg-qw8e">2.937</td>
    <td class="tg-qw8e">3.261</td>
    <td class="tg-qw8e">3.496</td>
  </tr>
  <tr>
    <td class="tg-oaw3">60</td>
    <td class="tg-1lb8">0.679</td>
    <td class="tg-1lb8">0.848</td>
    <td class="tg-1lb8">1.045</td>
    <td class="tg-1lb8">1.296</td>
    <td class="tg-1lb8">1.671</td>
    <td class="tg-1lb8">2.000</td>
    <td class="tg-1lb8">2.099</td>
    <td class="tg-1lb8">2.390</td>
    <td class="tg-1lb8">2.660</td>
    <td class="tg-1lb8">2.915</td>
    <td class="tg-1lb8">3.232</td>
    <td class="tg-1lb8">3.460</td>
  </tr>
  <tr>
    <td class="tg-oaw3">80</td>
    <td class="tg-qw8e">0.678</td>
    <td class="tg-qw8e">0.846</td>
    <td class="tg-qw8e">1.043</td>
    <td class="tg-qw8e">1.292</td>
    <td class="tg-qw8e">1.664</td>
    <td class="tg-qw8e">1.990</td>
    <td class="tg-qw8e">2.088</td>
    <td class="tg-qw8e">2.374</td>
    <td class="tg-qw8e">2.639</td>
    <td class="tg-qw8e">2.887</td>
    <td class="tg-qw8e">3.195</td>
    <td class="tg-qw8e">3.416</td>
  </tr>
  <tr>
    <td class="tg-oaw3">100</td>
    <td class="tg-1lb8">0.677</td>
    <td class="tg-1lb8">0.845</td>
    <td class="tg-1lb8">1.042</td>
    <td class="tg-1lb8">1.290</td>
    <td class="tg-1lb8">1.660</td>
    <td class="tg-1lb8">1.984</td>
    <td class="tg-1lb8">2.081</td>
    <td class="tg-1lb8">2.364</td>
    <td class="tg-1lb8">2.626</td>
    <td class="tg-1lb8">2.871</td>
    <td class="tg-1lb8">3.174</td>
    <td class="tg-1lb8">3.390</td>
  </tr>
  <tr>
    <td class="tg-oaw3">1000</td>
    <td class="tg-qw8e">0.675</td>
    <td class="tg-qw8e">0.842</td>
    <td class="tg-qw8e">1.037</td>
    <td class="tg-qw8e">1.282</td>
    <td class="tg-qw8e">1.646</td>
    <td class="tg-qw8e">1.962</td>
    <td class="tg-qw8e">2.056</td>
    <td class="tg-qw8e">2.330</td>
    <td class="tg-qw8e">2.581</td>
    <td class="tg-qw8e">2.813</td>
    <td class="tg-qw8e">3.098</td>
    <td class="tg-qw8e">3.300</td>
  </tr>
  <tr>
    <td class="tg-oaw3">$\infty$</td>
    <td class="tg-1lb8">0.674</td>
    <td class="tg-1lb8">0.842</td>
    <td class="tg-1lb8">1.036</td>
    <td class="tg-1lb8">1.282</td>
    <td class="tg-1lb8">1.645</td>
    <td class="tg-1lb8">1.960</td>
    <td class="tg-1lb8">2.054</td>
    <td class="tg-1lb8">2.326</td>
    <td class="tg-1lb8">2.576</td>
    <td class="tg-1lb8">2.807</td>
    <td class="tg-1lb8">3.090</td>
    <td class="tg-1lb8">3.291</td>
  </tr>
  <tr>
    <td class="tg-hp4q"></td>
    <td class="tg-g5p5">50%</td>
    <td class="tg-g5p5">60%</td>
    <td class="tg-g5p5">70%</td>
    <td class="tg-g5p5">80%</td>
    <td class="tg-g5p5">90%</td>
    <td class="tg-g5p5">95%</td>
    <td class="tg-g5p5">96%</td>
    <td class="tg-g5p5">98%</td>
    <td class="tg-g5p5">99%</td>
    <td class="tg-g5p5">99.50%</td>
    <td class="tg-g5p5">99.8</td>
    <td class="tg-g5p5">99.99%</td>
  </tr>
  <tr>
    <td class="tg-g5p5" colspan="13">Confidence Level $C$</td>
  </tr>
</tbody>
</table>

</details>


## Table C: $\chi^2$ critical values {#table-c}

```{r chisq dist table, echo = FALSE, warning = FALSE}
chidf <- function(x) dchisq(x, df = 4)

ggplot() +
    geom_polygon(aes(x = c(7, seq(7,11,0.01), 11), y = c(0, chidf(seq(7,11,0.01)), 0)), alpha = 0.5) +
    stat_function(fun = chidf, xlim = c(0, 11), size = 1.2, n = 1000) + theme_void() +
    annotate("segment", x = 7, xend = 7, y = -.005, yend = .005, size = 1.1) + 
    annotate("text", x = 7, y = -.01, label = expression(chi^2)) +
    annotate("segment", x = 9, y = .075, xend = 8, yend = .015, arrow = arrow(), size = 1.1) +
    annotate("text", x = 9, y = 0.09, label =  "Probability p")

# x.4 <- seq(7,11,0.01)
# par(mar=c(3,1,1,1))
# plot.new()
# plot.window(c(0, 11), c(0, .2))
# chidf <- function(x) dchisq(x, df = 4)
# curve(chidf, lwd = 1.5, add=TRUE)
# polygon(c(7, x.4, 11), c(0, chidf(x.4), 0), col = "gray")
# axis(side = 1, at = 7, labels = expression(chi^2))
# arrows(9, .075, 8, .015, lwd = 1.5)
# text(9, .09, "Probability p")
# box()
```

```{r chisq table calc, echo = FALSE}
# dfs <- c(1:30, 40, 50, 60, 80, 100)
# ps <- c(.25, .2, .15, .1, .05, .025, .02, .01, .005, .0025, .001, .0005)
# 
# chi_sq_vals_df = data.frame(replicate(12, numeric(35)))
# 
# rownames(chi_sq_vals_df) <- dfs
# colnames(chi_sq_vals_df) <- ps
# 
# for (p in ps) {
#     chi_sq_vals_df[[paste(p)]] <- qchisq(p, dfs, lower.tail = FALSE)
# }
# 
# write.csv(chi_sq_vals_df, "chi_sq_vals_df.csv")
```

<details>
<summary> Click here for table of $\chi^2$ distribution critical values </summary>

Table entry for $p$ is the point ($\chi^2$) with probability $p$ lying above it.

<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;}
.tg td{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  overflow:hidden;padding:10px 5px;word-break:normal;}
.tg th{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-fpgh{background-color:#C0C0C0;font-family:"Lucida Console", Monaco, monospace !important;text-align:left;vertical-align:top}
.tg .tg-4e5m{background-color:#343434;color:#FFF;font-family:"Lucida Console", Monaco, monospace !important;font-weight:bold;
  text-align:center;vertical-align:top}
.tg .tg-x5s5{font-family:"Lucida Console", Monaco, monospace !important;text-align:center;vertical-align:top}
.tg .tg-o5ql{background-color:#FFF;font-family:"Lucida Console", Monaco, monospace !important;font-weight:bold;text-align:center;
  vertical-align:bottom}
.tg .tg-e6u5{background-color:#FFF;font-family:"Lucida Console", Monaco, monospace !important;font-weight:bold;text-align:center;
  vertical-align:top}
.tg .tg-n0cl{background-color:#343434;color:#FFF;font-family:"Lucida Console", Monaco, monospace !important;text-align:center;
  vertical-align:top}
</style>
<table class="tg">
<thead>
  <tr>
    <th class="tg-o5ql" rowspan="2">df</th>
    <th class="tg-e6u5" colspan="12">Tail Probability $p$</th>
  </tr>
  <tr>
    <th class="tg-4e5m">0.25</th>
    <th class="tg-4e5m">0.20</th>
    <th class="tg-4e5m">0.15</th>
    <th class="tg-4e5m">0.10</th>
    <th class="tg-4e5m">0.05</th>
    <th class="tg-4e5m">0.025</th>
    <th class="tg-4e5m">0.02</th>
    <th class="tg-4e5m">0.01</th>
    <th class="tg-4e5m">0.005</th>
    <th class="tg-4e5m">0.0025</th>
    <th class="tg-4e5m">0.001</th>
    <th class="tg-4e5m">0.0005</th>
  </tr>
</thead>
<tbody>
  <tr>
    <td class="tg-n0cl">1</td>
    <td class="tg-x5s5">1.32</td>
    <td class="tg-x5s5">1.64</td>
    <td class="tg-x5s5">2.07</td>
    <td class="tg-x5s5">2.71</td>
    <td class="tg-x5s5">3.84</td>
    <td class="tg-x5s5">5.02</td>
    <td class="tg-x5s5">5.41</td>
    <td class="tg-x5s5">6.63</td>
    <td class="tg-x5s5">7.88</td>
    <td class="tg-x5s5">9.14</td>
    <td class="tg-x5s5">10.83</td>
    <td class="tg-x5s5">12.12</td>
  </tr>
  <tr>
    <td class="tg-n0cl">2</td>
    <td class="tg-fpgh">2.77</td>
    <td class="tg-fpgh">3.22</td>
    <td class="tg-fpgh">3.79</td>
    <td class="tg-fpgh">4.61</td>
    <td class="tg-fpgh">5.99</td>
    <td class="tg-fpgh">7.38</td>
    <td class="tg-fpgh">7.82</td>
    <td class="tg-fpgh">9.21</td>
    <td class="tg-fpgh">10.60</td>
    <td class="tg-fpgh">11.98</td>
    <td class="tg-fpgh">13.82</td>
    <td class="tg-fpgh">15.20</td>
  </tr>
  <tr>
    <td class="tg-n0cl">3</td>
    <td class="tg-x5s5">4.11</td>
    <td class="tg-x5s5">4.64</td>
    <td class="tg-x5s5">5.32</td>
    <td class="tg-x5s5">6.25</td>
    <td class="tg-x5s5">7.81</td>
    <td class="tg-x5s5">9.35</td>
    <td class="tg-x5s5">9.84</td>
    <td class="tg-x5s5">11.34</td>
    <td class="tg-x5s5">12.84</td>
    <td class="tg-x5s5">14.32</td>
    <td class="tg-x5s5">16.27</td>
    <td class="tg-x5s5">17.73</td>
  </tr>
  <tr>
    <td class="tg-n0cl">4</td>
    <td class="tg-fpgh">5.39</td>
    <td class="tg-fpgh">5.99</td>
    <td class="tg-fpgh">6.74</td>
    <td class="tg-fpgh">7.78</td>
    <td class="tg-fpgh">9.49</td>
    <td class="tg-fpgh">11.14</td>
    <td class="tg-fpgh">11.67</td>
    <td class="tg-fpgh">13.28</td>
    <td class="tg-fpgh">14.86</td>
    <td class="tg-fpgh">16.42</td>
    <td class="tg-fpgh">18.47</td>
    <td class="tg-fpgh">20.00</td>
  </tr>
  <tr>
    <td class="tg-n0cl">5</td>
    <td class="tg-x5s5">6.63</td>
    <td class="tg-x5s5">7.29</td>
    <td class="tg-x5s5">8.12</td>
    <td class="tg-x5s5">9.24</td>
    <td class="tg-x5s5">11.07</td>
    <td class="tg-x5s5">12.83</td>
    <td class="tg-x5s5">13.39</td>
    <td class="tg-x5s5">15.09</td>
    <td class="tg-x5s5">16.75</td>
    <td class="tg-x5s5">18.39</td>
    <td class="tg-x5s5">20.52</td>
    <td class="tg-x5s5">22.11</td>
  </tr>
  <tr>
    <td class="tg-n0cl">6</td>
    <td class="tg-fpgh">7.84</td>
    <td class="tg-fpgh">8.56</td>
    <td class="tg-fpgh">9.45</td>
    <td class="tg-fpgh">10.64</td>
    <td class="tg-fpgh">12.59</td>
    <td class="tg-fpgh">14.45</td>
    <td class="tg-fpgh">15.03</td>
    <td class="tg-fpgh">16.81</td>
    <td class="tg-fpgh">18.55</td>
    <td class="tg-fpgh">20.25</td>
    <td class="tg-fpgh">22.46</td>
    <td class="tg-fpgh">24.10</td>
  </tr>
  <tr>
    <td class="tg-n0cl">7</td>
    <td class="tg-x5s5">9.04</td>
    <td class="tg-x5s5">9.80</td>
    <td class="tg-x5s5">10.75</td>
    <td class="tg-x5s5">12.02</td>
    <td class="tg-x5s5">14.07</td>
    <td class="tg-x5s5">16.01</td>
    <td class="tg-x5s5">16.62</td>
    <td class="tg-x5s5">18.48</td>
    <td class="tg-x5s5">20.28</td>
    <td class="tg-x5s5">22.04</td>
    <td class="tg-x5s5">24.32</td>
    <td class="tg-x5s5">26.02</td>
  </tr>
  <tr>
    <td class="tg-n0cl">8</td>
    <td class="tg-fpgh">10.22</td>
    <td class="tg-fpgh">11.03</td>
    <td class="tg-fpgh">12.03</td>
    <td class="tg-fpgh">13.36</td>
    <td class="tg-fpgh">15.51</td>
    <td class="tg-fpgh">17.53</td>
    <td class="tg-fpgh">18.17</td>
    <td class="tg-fpgh">20.09</td>
    <td class="tg-fpgh">21.95</td>
    <td class="tg-fpgh">23.77</td>
    <td class="tg-fpgh">26.12</td>
    <td class="tg-fpgh">27.87</td>
  </tr>
  <tr>
    <td class="tg-n0cl">9</td>
    <td class="tg-x5s5">11.39</td>
    <td class="tg-x5s5">12.24</td>
    <td class="tg-x5s5">13.29</td>
    <td class="tg-x5s5">14.68</td>
    <td class="tg-x5s5">16.92</td>
    <td class="tg-x5s5">19.02</td>
    <td class="tg-x5s5">19.68</td>
    <td class="tg-x5s5">21.67</td>
    <td class="tg-x5s5">23.59</td>
    <td class="tg-x5s5">25.46</td>
    <td class="tg-x5s5">27.88</td>
    <td class="tg-x5s5">29.67</td>
  </tr>
  <tr>
    <td class="tg-n0cl">10</td>
    <td class="tg-fpgh">12.55</td>
    <td class="tg-fpgh">13.44</td>
    <td class="tg-fpgh">14.53</td>
    <td class="tg-fpgh">15.99</td>
    <td class="tg-fpgh">18.31</td>
    <td class="tg-fpgh">20.48</td>
    <td class="tg-fpgh">21.16</td>
    <td class="tg-fpgh">23.21</td>
    <td class="tg-fpgh">25.19</td>
    <td class="tg-fpgh">27.11</td>
    <td class="tg-fpgh">29.59</td>
    <td class="tg-fpgh">31.42</td>
  </tr>
  <tr>
    <td class="tg-n0cl">11</td>
    <td class="tg-x5s5">13.70</td>
    <td class="tg-x5s5">14.63</td>
    <td class="tg-x5s5">15.77</td>
    <td class="tg-x5s5">17.28</td>
    <td class="tg-x5s5">19.68</td>
    <td class="tg-x5s5">21.92</td>
    <td class="tg-x5s5">22.62</td>
    <td class="tg-x5s5">24.72</td>
    <td class="tg-x5s5">26.76</td>
    <td class="tg-x5s5">28.73</td>
    <td class="tg-x5s5">31.26</td>
    <td class="tg-x5s5">33.14</td>
  </tr>
  <tr>
    <td class="tg-n0cl">12</td>
    <td class="tg-fpgh">14.85</td>
    <td class="tg-fpgh">15.81</td>
    <td class="tg-fpgh">16.99</td>
    <td class="tg-fpgh">18.55</td>
    <td class="tg-fpgh">21.03</td>
    <td class="tg-fpgh">23.34</td>
    <td class="tg-fpgh">24.05</td>
    <td class="tg-fpgh">26.22</td>
    <td class="tg-fpgh">28.30</td>
    <td class="tg-fpgh">30.32</td>
    <td class="tg-fpgh">32.91</td>
    <td class="tg-fpgh">34.82</td>
  </tr>
  <tr>
    <td class="tg-n0cl">13</td>
    <td class="tg-x5s5">15.98</td>
    <td class="tg-x5s5">16.98</td>
    <td class="tg-x5s5">18.20</td>
    <td class="tg-x5s5">19.81</td>
    <td class="tg-x5s5">22.36</td>
    <td class="tg-x5s5">24.74</td>
    <td class="tg-x5s5">25.47</td>
    <td class="tg-x5s5">27.69</td>
    <td class="tg-x5s5">29.82</td>
    <td class="tg-x5s5">31.88</td>
    <td class="tg-x5s5">34.53</td>
    <td class="tg-x5s5">36.48</td>
  </tr>
  <tr>
    <td class="tg-n0cl">14</td>
    <td class="tg-fpgh">17.12</td>
    <td class="tg-fpgh">18.15</td>
    <td class="tg-fpgh">19.41</td>
    <td class="tg-fpgh">21.06</td>
    <td class="tg-fpgh">23.68</td>
    <td class="tg-fpgh">26.12</td>
    <td class="tg-fpgh">26.87</td>
    <td class="tg-fpgh">29.14</td>
    <td class="tg-fpgh">31.32</td>
    <td class="tg-fpgh">33.43</td>
    <td class="tg-fpgh">36.12</td>
    <td class="tg-fpgh">38.11</td>
  </tr>
  <tr>
    <td class="tg-n0cl">15</td>
    <td class="tg-x5s5">18.25</td>
    <td class="tg-x5s5">19.31</td>
    <td class="tg-x5s5">20.60</td>
    <td class="tg-x5s5">22.31</td>
    <td class="tg-x5s5">25.00</td>
    <td class="tg-x5s5">27.49</td>
    <td class="tg-x5s5">28.26</td>
    <td class="tg-x5s5">30.58</td>
    <td class="tg-x5s5">32.80</td>
    <td class="tg-x5s5">34.95</td>
    <td class="tg-x5s5">37.70</td>
    <td class="tg-x5s5">39.72</td>
  </tr>
  <tr>
    <td class="tg-n0cl">16</td>
    <td class="tg-fpgh">19.37</td>
    <td class="tg-fpgh">20.47</td>
    <td class="tg-fpgh">21.79</td>
    <td class="tg-fpgh">23.54</td>
    <td class="tg-fpgh">26.30</td>
    <td class="tg-fpgh">28.85</td>
    <td class="tg-fpgh">29.63</td>
    <td class="tg-fpgh">32.00</td>
    <td class="tg-fpgh">34.27</td>
    <td class="tg-fpgh">36.46</td>
    <td class="tg-fpgh">39.25</td>
    <td class="tg-fpgh">41.31</td>
  </tr>
  <tr>
    <td class="tg-n0cl">17</td>
    <td class="tg-x5s5">20.49</td>
    <td class="tg-x5s5">21.61</td>
    <td class="tg-x5s5">22.98</td>
    <td class="tg-x5s5">24.77</td>
    <td class="tg-x5s5">27.59</td>
    <td class="tg-x5s5">30.19</td>
    <td class="tg-x5s5">31.00</td>
    <td class="tg-x5s5">33.41</td>
    <td class="tg-x5s5">35.72</td>
    <td class="tg-x5s5">37.95</td>
    <td class="tg-x5s5">40.79</td>
    <td class="tg-x5s5">42.88</td>
  </tr>
  <tr>
    <td class="tg-n0cl">18</td>
    <td class="tg-fpgh">21.60</td>
    <td class="tg-fpgh">22.76</td>
    <td class="tg-fpgh">24.16</td>
    <td class="tg-fpgh">25.99</td>
    <td class="tg-fpgh">28.87</td>
    <td class="tg-fpgh">31.53</td>
    <td class="tg-fpgh">32.35</td>
    <td class="tg-fpgh">34.81</td>
    <td class="tg-fpgh">37.16</td>
    <td class="tg-fpgh">39.42</td>
    <td class="tg-fpgh">42.31</td>
    <td class="tg-fpgh">44.43</td>
  </tr>
  <tr>
    <td class="tg-n0cl">19</td>
    <td class="tg-x5s5">22.72</td>
    <td class="tg-x5s5">23.90</td>
    <td class="tg-x5s5">25.33</td>
    <td class="tg-x5s5">27.20</td>
    <td class="tg-x5s5">30.14</td>
    <td class="tg-x5s5">32.85</td>
    <td class="tg-x5s5">33.69</td>
    <td class="tg-x5s5">36.19</td>
    <td class="tg-x5s5">38.58</td>
    <td class="tg-x5s5">40.88</td>
    <td class="tg-x5s5">43.82</td>
    <td class="tg-x5s5">45.97</td>
  </tr>
  <tr>
    <td class="tg-n0cl">20</td>
    <td class="tg-fpgh">23.83</td>
    <td class="tg-fpgh">25.04</td>
    <td class="tg-fpgh">26.50</td>
    <td class="tg-fpgh">28.41</td>
    <td class="tg-fpgh">31.41</td>
    <td class="tg-fpgh">34.17</td>
    <td class="tg-fpgh">35.02</td>
    <td class="tg-fpgh">37.57</td>
    <td class="tg-fpgh">40.00</td>
    <td class="tg-fpgh">42.34</td>
    <td class="tg-fpgh">45.31</td>
    <td class="tg-fpgh">47.50</td>
  </tr>
  <tr>
    <td class="tg-n0cl">21</td>
    <td class="tg-x5s5">24.93</td>
    <td class="tg-x5s5">26.17</td>
    <td class="tg-x5s5">27.66</td>
    <td class="tg-x5s5">29.62</td>
    <td class="tg-x5s5">32.67</td>
    <td class="tg-x5s5">35.48</td>
    <td class="tg-x5s5">36.34</td>
    <td class="tg-x5s5">38.93</td>
    <td class="tg-x5s5">41.40</td>
    <td class="tg-x5s5">43.78</td>
    <td class="tg-x5s5">46.80</td>
    <td class="tg-x5s5">49.01</td>
  </tr>
  <tr>
    <td class="tg-n0cl">22</td>
    <td class="tg-fpgh">26.04</td>
    <td class="tg-fpgh">27.30</td>
    <td class="tg-fpgh">28.82</td>
    <td class="tg-fpgh">30.81</td>
    <td class="tg-fpgh">33.92</td>
    <td class="tg-fpgh">36.78</td>
    <td class="tg-fpgh">37.66</td>
    <td class="tg-fpgh">40.29</td>
    <td class="tg-fpgh">42.80</td>
    <td class="tg-fpgh">45.20</td>
    <td class="tg-fpgh">48.27</td>
    <td class="tg-fpgh">50.51</td>
  </tr>
  <tr>
    <td class="tg-n0cl">23</td>
    <td class="tg-x5s5">27.14</td>
    <td class="tg-x5s5">28.43</td>
    <td class="tg-x5s5">29.98</td>
    <td class="tg-x5s5">32.01</td>
    <td class="tg-x5s5">35.17</td>
    <td class="tg-x5s5">38.08</td>
    <td class="tg-x5s5">38.97</td>
    <td class="tg-x5s5">41.64</td>
    <td class="tg-x5s5">44.18</td>
    <td class="tg-x5s5">46.62</td>
    <td class="tg-x5s5">49.73</td>
    <td class="tg-x5s5">52.00</td>
  </tr>
  <tr>
    <td class="tg-n0cl">24</td>
    <td class="tg-fpgh">28.24</td>
    <td class="tg-fpgh">29.55</td>
    <td class="tg-fpgh">31.13</td>
    <td class="tg-fpgh">33.20</td>
    <td class="tg-fpgh">36.42</td>
    <td class="tg-fpgh">39.36</td>
    <td class="tg-fpgh">40.27</td>
    <td class="tg-fpgh">42.98</td>
    <td class="tg-fpgh">45.56</td>
    <td class="tg-fpgh">48.03</td>
    <td class="tg-fpgh">51.18</td>
    <td class="tg-fpgh">53.48</td>
  </tr>
  <tr>
    <td class="tg-n0cl">25</td>
    <td class="tg-x5s5">29.34</td>
    <td class="tg-x5s5">30.68</td>
    <td class="tg-x5s5">32.28</td>
    <td class="tg-x5s5">34.38</td>
    <td class="tg-x5s5">37.65</td>
    <td class="tg-x5s5">40.65</td>
    <td class="tg-x5s5">41.57</td>
    <td class="tg-x5s5">44.31</td>
    <td class="tg-x5s5">46.93</td>
    <td class="tg-x5s5">49.44</td>
    <td class="tg-x5s5">52.62</td>
    <td class="tg-x5s5">54.95</td>
  </tr>
  <tr>
    <td class="tg-n0cl">26</td>
    <td class="tg-fpgh">30.43</td>
    <td class="tg-fpgh">31.79</td>
    <td class="tg-fpgh">33.43</td>
    <td class="tg-fpgh">35.56</td>
    <td class="tg-fpgh">38.89</td>
    <td class="tg-fpgh">41.92</td>
    <td class="tg-fpgh">42.86</td>
    <td class="tg-fpgh">45.64</td>
    <td class="tg-fpgh">48.29</td>
    <td class="tg-fpgh">50.83</td>
    <td class="tg-fpgh">54.05</td>
    <td class="tg-fpgh">56.41</td>
  </tr>
  <tr>
    <td class="tg-n0cl">27</td>
    <td class="tg-x5s5">31.53</td>
    <td class="tg-x5s5">32.91</td>
    <td class="tg-x5s5">34.57</td>
    <td class="tg-x5s5">36.74</td>
    <td class="tg-x5s5">40.11</td>
    <td class="tg-x5s5">43.19</td>
    <td class="tg-x5s5">44.14</td>
    <td class="tg-x5s5">46.96</td>
    <td class="tg-x5s5">49.64</td>
    <td class="tg-x5s5">52.22</td>
    <td class="tg-x5s5">55.48</td>
    <td class="tg-x5s5">57.86</td>
  </tr>
  <tr>
    <td class="tg-n0cl">28</td>
    <td class="tg-fpgh">32.62</td>
    <td class="tg-fpgh">34.03</td>
    <td class="tg-fpgh">35.71</td>
    <td class="tg-fpgh">37.92</td>
    <td class="tg-fpgh">41.34</td>
    <td class="tg-fpgh">44.46</td>
    <td class="tg-fpgh">45.42</td>
    <td class="tg-fpgh">48.28</td>
    <td class="tg-fpgh">50.99</td>
    <td class="tg-fpgh">53.59</td>
    <td class="tg-fpgh">56.89</td>
    <td class="tg-fpgh">59.30</td>
  </tr>
  <tr>
    <td class="tg-n0cl">29</td>
    <td class="tg-x5s5">33.71</td>
    <td class="tg-x5s5">35.14</td>
    <td class="tg-x5s5">36.85</td>
    <td class="tg-x5s5">39.09</td>
    <td class="tg-x5s5">42.56</td>
    <td class="tg-x5s5">45.72</td>
    <td class="tg-x5s5">46.69</td>
    <td class="tg-x5s5">49.59</td>
    <td class="tg-x5s5">52.34</td>
    <td class="tg-x5s5">54.97</td>
    <td class="tg-x5s5">58.30</td>
    <td class="tg-x5s5">60.73</td>
  </tr>
  <tr>
    <td class="tg-n0cl">30</td>
    <td class="tg-fpgh">34.80</td>
    <td class="tg-fpgh">36.25</td>
    <td class="tg-fpgh">37.99</td>
    <td class="tg-fpgh">40.26</td>
    <td class="tg-fpgh">43.77</td>
    <td class="tg-fpgh">46.98</td>
    <td class="tg-fpgh">47.96</td>
    <td class="tg-fpgh">50.89</td>
    <td class="tg-fpgh">53.67</td>
    <td class="tg-fpgh">56.33</td>
    <td class="tg-fpgh">59.70</td>
    <td class="tg-fpgh">62.16</td>
  </tr>
  <tr>
    <td class="tg-n0cl">40</td>
    <td class="tg-x5s5">45.62</td>
    <td class="tg-x5s5">47.27</td>
    <td class="tg-x5s5">49.24</td>
    <td class="tg-x5s5">51.81</td>
    <td class="tg-x5s5">55.76</td>
    <td class="tg-x5s5">59.34</td>
    <td class="tg-x5s5">60.44</td>
    <td class="tg-x5s5">63.69</td>
    <td class="tg-x5s5">66.77</td>
    <td class="tg-x5s5">69.70</td>
    <td class="tg-x5s5">73.40</td>
    <td class="tg-x5s5">76.09</td>
  </tr>
  <tr>
    <td class="tg-n0cl">50</td>
    <td class="tg-fpgh">56.33</td>
    <td class="tg-fpgh">58.16</td>
    <td class="tg-fpgh">60.35</td>
    <td class="tg-fpgh">63.17</td>
    <td class="tg-fpgh">67.50</td>
    <td class="tg-fpgh">71.42</td>
    <td class="tg-fpgh">72.61</td>
    <td class="tg-fpgh">76.15</td>
    <td class="tg-fpgh">79.49</td>
    <td class="tg-fpgh">82.66</td>
    <td class="tg-fpgh">86.66</td>
    <td class="tg-fpgh">89.56</td>
  </tr>
  <tr>
    <td class="tg-n0cl">60</td>
    <td class="tg-x5s5">66.98</td>
    <td class="tg-x5s5">68.97</td>
    <td class="tg-x5s5">71.34</td>
    <td class="tg-x5s5">74.40</td>
    <td class="tg-x5s5">79.08</td>
    <td class="tg-x5s5">83.30</td>
    <td class="tg-x5s5">84.58</td>
    <td class="tg-x5s5">88.38</td>
    <td class="tg-x5s5">91.95</td>
    <td class="tg-x5s5">95.34</td>
    <td class="tg-x5s5">99.61</td>
    <td class="tg-x5s5">102.69</td>
  </tr>
  <tr>
    <td class="tg-n0cl">80</td>
    <td class="tg-fpgh">88.13</td>
    <td class="tg-fpgh">90.41</td>
    <td class="tg-fpgh">93.11</td>
    <td class="tg-fpgh">96.58</td>
    <td class="tg-fpgh">101.9</td>
    <td class="tg-fpgh">106.6</td>
    <td class="tg-fpgh">108.1</td>
    <td class="tg-fpgh">112.3</td>
    <td class="tg-fpgh">116.3</td>
    <td class="tg-fpgh">120.1</td>
    <td class="tg-fpgh">124.8</td>
    <td class="tg-fpgh">128.3</td>
  </tr>
  <tr>
    <td class="tg-n0cl">100</td>
    <td class="tg-x5s5">109.1</td>
    <td class="tg-x5s5">111.7</td>
    <td class="tg-x5s5">114.7</td>
    <td class="tg-x5s5">118.5</td>
    <td class="tg-x5s5">124.3</td>
    <td class="tg-x5s5">129.6</td>
    <td class="tg-x5s5">131.1</td>
    <td class="tg-x5s5">135.8</td>
    <td class="tg-x5s5">140.2</td>
    <td class="tg-x5s5">144.3</td>
    <td class="tg-x5s5">149.4</td>
    <td class="tg-x5s5">153.2</td>
  </tr>
</tbody>
</table>

</details>
