--- 
title: "AP Statistics Notes"
author: "Mr. Chang `edwardchang@berkeley.net`"
institute: "Berkeley High School"
date: "`r Sys.Date()`"
output:
    bookdown::bs4_book:
        theme:
            primary: "#6A5ACD"   # default .rmdnote = blue
            danger:  "#dc3545"   # default .rmdcaution = red
            success: "#198754"   # default .rmdimportant = green
            info:    "#0dcaf0"   # default .rmdtip = cyan
            warning: "#ffc107"   # default .rmdwarning = yellow
        config:
            sharing: no
site: bookdown::bookdown_site
documentclass: book
url: https://stats.echa.ng
description: |
  These are notes for AP Statistics.
link-citations: yes
always_allow_html: true
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, fig.path = "images/")
```

```{r, message = FALSE, warning = FALSE}
table_show = rmarkdown::paged_table
library(tidyverse)
library(knitr)
```

# Introduction

These are my notes based off what we learned in class.

There are various functions on this website that make your notes accessible in the case that you need more support in reading the material. Take a look at the tool bar on the top and try right clicking on math equations to see options to enlargen math equations. Ask Mr. Chang if you want to explore more.

These notes are incomplete, but I'll be trying to update them completely before the AP test. Give me any feedback that you might want to see on these notes.

Look at the rest of these notes through the navigation bar on the left hand side (might have to click on the hamburger icon), or go through these sequentially by clicking the arrows on the left and right hand side.
