# Quantative Data Visualizations

```{r}
library(tidyverse)
```

## Dot Plots

::: {.callout-note title="Dot Plots"}
Dots Plots represent one quantitative variable by marking a dot for each value observed. 
They are mainly for discrete quantitative variables only and they are
mainly useful in situations when you have a small range of number so that
you can actually see how the data distribution varies across values.
:::

Dot plots are simple, you draw a number line and then plot points above
the number for each of the number that you see in the data.

Take this data for example:

```{r student-table}
set.seed(123)
(X <- data.frame(`Number of Students in the Hallway` = round(rnorm(20, 5, 2))))
```

Now count up each value to figure out how many dots you need at each
value on the number line then plot your graph

```{r student-dot-plot}
as_tibble(table(X), colnames = c("Number of People", "Frequency"))
ggplot(X, aes(x = Number.of.Students.in.the.Hallway, y = ..count..)) + geom_dotplot() +
    scale_x_continuous(breaks = 1:9, labels = 1:9) +
    labs(y = "Frequency", title = "Dot Plot of the Number of People in the Hallway")
```

## Stemplots

::: {.callout-note title="Stemplots"}
In a stem plot, you need to determine a common "stem" of all the numbers
that you're plotting. So if you have integer numbers from 10 to 200,
your stems will be everything from the tens and so on, so you'll have
stems from 1-20. Once you take the stems, you just write the "leaves"
next to the stem that they belong.

These are also known as stem-and-leaf plots.
:::

Using this data as an example,

```{r stemplot-data}
set.seed(123)
x <- round(rnorm(20, 50, 25))
data.frame(x)
```

A stem plot looks like this:

```{r stemplot-pic}
library(aplpack)
stem.leaf(x, style = "bare", depths = FALSE)
```

::: {.callout-important}
Note that you also have to add a key to show what a stem + leaf means.
The stem and leaves give no information on the decimals in the data, so
as you see above, you need to give an example like (as shown in the
example stemplot):

    Key: 1\|2 = 12
:::

Here's another example (sorted for convenience)

```{r stemplot-pic-2}
x <- round(rnorm(50, 5, 1), digits = 1)
data.frame(x)
stem.leaf(x, style = "bare", depths = FALSE)
```

## Boxplots

::: {.callout-note title="Boxplots"}
Boxplots are primarily made of the **five number summary** of the data.
The five number summary is made up of the:

1. Minimum (min)
2. First Quartile ($Q_1$)
3. Median
4. Third Quartile ($Q_3$)
5. Maximum (max)

Also known as a box-and-whisker plot.
:::

To make a simple boxplot, you use the first quartile, median, and third
quartile to make the "box" and then use the minimum and maximum to make
the "whiskers."

For this simple list of numbers:

```{r simple-x}
x = c(1,2,3,4,5,6,7)
data.frame(x)

```

Our five number summary is:

```{r simple-5ns}
summary(x, quantile.type = 1)[-4]
```

As detailed above, our box plot then looks like:

```{r simple-boxplot}
#| fig-height: 2
ggplot(data.frame(x)) +
    geom_boxplot(aes(x = x))
```

::: {.callout-important}
The last detail is that we can calculate outliers using the 1.5 IQR rule
and show them on the boxplot. For either direction (left or right), if
we see outliers in that direction, we only extend the whisker to the
smallest and/or largest point that is not an outlier. Then we plot any
outliers as individual points.
:::

Look at this example data:

```{r adv-boxplot-data}
set.seed(1234)
x <- round(rnorm(40, 0, 5))
arrange(data.frame(x), desc(x))
```

Five number summary:

```{r adv-5ns}
summary(x, quantile.type = 1)[-4]
```

Our numbers calculated by the 1.5 IQR rule are:

```{r adv-iqr}
c(-5, 0) + 1.5 * c(-5, 5)
```

So our 12 is an outlier. which means we draw our right whisker to 6 and
plot the 12 individually on the number line. Like so:

```{r Advanced Box Plot}
#| fig-height: 2
ggplot(data.frame(x)) +
    geom_boxplot(aes(x = x))
```

## Histograms

::: {.callout-note title="Histograms"}
A histogram is similar to a [bar plot](#bar-plots), except that
histograms are made for quantitative data and *bars are continuous* in
the sense that there is no gap between bars. To make a histogram, select
an appropriate equal intervals that make it so that you don't have too
many bars and that you don't have too few bars.
:::

::: {.callout-tip}
Your goal with
histograms, as with many other visualizations, is to be able to see the
shape and characteristics of the distribution in question. If you have
too many bars or too few bars, you won't be able to see much important
information (especially think of situations when you have many data
points with very precise decimal measurements).
:::


1.  Decide on your intervals (e.g. by 5's, by 10's, by 100's)
2.  Within your intervals, count up the number of observations that
    belong in that "bin". When you do so, count up observations so that
    you count the left end inclusive and the right end inclusive. So if
    you did intervals of 5, you would do something like counting up
    points $0 \leq x < 5$, $5 \leq x < 10$, and so on.
3.  Plot your bars.

Example:

Consider this example data set:

```{r}
ex_data <- data.frame(x = log(rnorm(20, 10, 3)))
```

Our data has this set of summary statistics:

```{r}
summary(ex_data)
```

With this knowledge, let's make our 7 "bins", so let's do these by every
0.2, starting at 1.5 to 2.9. This will be something that you build by
intuition.

Now, count up our values:

```{r}
summary(cut(ex_data$x, breaks = seq(1.5, 2.9, 0.2), include.lowest = TRUE, right = FALSE))
```

Now, we just put it together. For each bin, we have a bar and the bars'
heights correspond to the number of individuals in each bin.

```{r}
ggplot(ex_data, aes(x = x)) + geom_histogram(breaks = seq(1.5, 2.9, 0.2), color = "blue", alpha = 0.5) + scale_x_continuous(breaks = seq(1.5, 2.9, 0.2))
```

Again, just like bar graphs, we can instead do the relative frequencies
(this is what you'll see most of the time!!!)

```{r}
prop.table(summary(cut(ex_data$x, breaks = seq(1.5, 2.9, 0.2), include.lowest = TRUE, right = FALSE)))
```

```{r}
ggplot(ex_data, aes(x = x, y = ..density..)) + geom_histogram(breaks = seq(1.5, 2.9, 0.2), color = "blue", alpha = 0.5) + scale_x_continuous(breaks = seq(1.5, 2.9, 0.2))
```

::: {.callout-warning}
When you have a histogram like this, keep in mind that the bars always
add up to 1 (or 100%).
:::
